### 2022-01-01 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@ce51707d1363e9cdf30f88cfc0ba3fb1ace6a007 🚀

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}

\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences

\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

This template uses \texttt{pandoc} (and a few additional python glue
scripts) to facilitate the production of scientific articles using a
standard markdown file. The objective is to ensure that standard
markdown (with the important exception of the \texttt{pandoc-crossref}
citation markup) will be rendered into an interactive website (which
allows collaborative annotations with the \texttt{hypothes.is}
platform), a ``draft'' style PDF (double-spaced, numbered lines, figures
at the end), and a ``preprint'' style PDF (with slightly more
reader-friendly pagination).

The core bit of configuration is the \texttt{metadata.json} file, which
handles information about authorship, affiliations, the abstract,
keywords, etc. All documents will be deployed to \texttt{gh-pages}
\emph{only} on push events from the \texttt{main} branch. All of the
artifacts will be built when doing pull requests, so you can check that
merging a branch is \emph{not} going to cause the compilation of the
documents to fail; indeed, you can download the artifacts produced
during the run, to check the PDF and html files. The website is only
updated from the \texttt{main} branch.

The workflow is \emph{very} GitHub based, and so the manuscript file
\emph{is} the \texttt{README.md} - this is not going to be a huge issue
as 90\% of the markdown is standard, with the exception of the citations
and mathematics, so this will render (mostly) like a normal README file.

\hypertarget{deploying-the-template}{%
\section{Deploying the template}\label{deploying-the-template}}

The process of deploying this template has been \emph{greatly}
streamlined from previous versions:

\begin{itemize}
\tightlist
\item
  Click on the ``Use this template'' button
\item
  Edit \texttt{README.md} with your own text, commit, and push
\item
  This push will trigger the first build - the builds are only active on
  the \texttt{main} branch (\emph{not} \texttt{master}!), and on pull
  requests
\item
  Go to \texttt{http://you.github.io/repo-name/} to view the html
  version, and get access to the PDFs
\item
  Add your references to the \texttt{references.bib} file
\item
  Edit the \texttt{metadata.json} file to add the title, abstract,
  authors
\end{itemize}

In particular, note that \emph{you do not need} to create a personnal
access token to deploy to \texttt{gh-pages} (from where the website is
served).

\hypertarget{the-metadata-file}{%
\section{The metadata file}\label{the-metadata-file}}

\hypertarget{general-information}{%
\subsection{General information}\label{general-information}}

The title is a field in the \texttt{metadata.json}:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{}
    \DataTypeTok{"title"}\FunctionTok{:} \StringTok{"Preprint template"}
\FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{authorship}{%
\subsection{Authorship}\label{authorship}}

Authors are listed as objects in the \texttt{authors} block. Each author
is specified as follows:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{}
      \DataTypeTok{"familyname"}\FunctionTok{:} \StringTok{"Bob"}\FunctionTok{,}
      \DataTypeTok{"givennames"}\FunctionTok{:} \StringTok{"Alice"}\FunctionTok{,}
      \DataTypeTok{"email"}\FunctionTok{:} \StringTok{"alice.bob@u.edu"}\FunctionTok{,}
      \DataTypeTok{"orcid"}\FunctionTok{:} \StringTok{"0000{-}0000{-}0000{-}0001"}\FunctionTok{,}
      \DataTypeTok{"affiliations"}\FunctionTok{:} \OtherTok{[}
        \StringTok{"Affiliation 1"}\OtherTok{,}
        \StringTok{"Affiliation 2"}
      \OtherTok{]}\FunctionTok{,}
      \DataTypeTok{"status"}\FunctionTok{:} \OtherTok{[}\StringTok{"corresponding"}\OtherTok{,} \StringTok{"equal"}\OtherTok{]}
    \FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

The \texttt{email} field is recommended for all authors. The
\texttt{status} field is only useful for the corresponding author, and
to denote equal contributions. These informations are rendered on the
initial page. If an \texttt{orcid} is given, it will be linked on the
HTML and PDF versions.

Note that there is \emph{no need} to number the affiliations - a small
python script will take care of this automatically.

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

This template supports three types of abstracts, indicated in the
metadata file as \texttt{abstract}:

A regular \texttt{abstract} is defined as

\begin{Shaded}
\begin{Highlighting}[]
\ErrorTok{"abstract":} \ErrorTok{"A} \ErrorTok{very} \ErrorTok{long} \ErrorTok{string"}
\end{Highlighting}
\end{Shaded}

An itemized abstract is an array of strings, each representing a bullet
point:

\begin{Shaded}
\begin{Highlighting}[]
\ErrorTok{"abstract":} \OtherTok{[}
    \StringTok{"Point 1"}\OtherTok{,}
    \StringTok{"Point 2"}
\OtherTok{]}
\end{Highlighting}
\end{Shaded}

A structured abstract is an object with key-value pairs :

\begin{Shaded}
\begin{Highlighting}[]
\ErrorTok{"abstract":} \FunctionTok{\{}
    \DataTypeTok{"Location"}\FunctionTok{:} \StringTok{"Worldwide"}\FunctionTok{,}
    \DataTypeTok{"Organisms"}\FunctionTok{:} \StringTok{"Mammals"}
\FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{citation-style}{%
\subsection{Citation style}\label{citation-style}}

The \texttt{citationstyle} key corresponds to the name, with
\texttt{.csl} ommited, of a CSL stylesheet stored in the
\href{https://github.com/citation-style-language/}{citation style
language} repository. Note that there is no difference between main and
dependent styles, the build engine will take the correct steps to get
the correct style. The default is
\texttt{"citationstyle":\ "ecology-letters"}. There is a longer section
about references management later on.

\hypertarget{references-management}{%
\section{References management}\label{references-management}}

The references are managed by \texttt{pandoc}. Note that we \emph{do
not} use \texttt{pandoc-citeproc}, which was an external module for
older \texttt{pandoc} versions. References \emph{must} be stored in a
\texttt{references.bib} file, and that it would make sense to order it
alphabetically by key.

We use \href{https://www.zotero.org/}{Zotero} for references management,
and for the lab's manuscripts, we work from folders in a shared library
(with a folder for every manuscript).

It is recommedned to use the
\href{https://retorque.re/zotero-better-bibtex/}{Better BibTeX} plugin
for citation key generations, and auto-export of the shared library to
the \texttt{references.bib} file. We use a citation key format meant to
convey information on the author (first author full name), date (complet
year), and title (first three letters of the first two non-stop words).
It must be set in the Better BibTeX preferences as (you might need to
remove the line changes):

\begin{verbatim}
[auth:fold]
[year]
[title:fold:nopunctordash:skipwords:lower:select=1,1:substring=1,3:capitalize]
[title:fold:nopunctordash:skipwords:lower:select=2,2:substring=1,3:capitalize]
\end{verbatim}

It is a good idea to configure Better BibTeX to auto-export on change,
and to remove a lot of fields that are not strictly speaking required
for references. The list of fields we usually ignore is:

\begin{verbatim}
abstract,copyright,annotation,file,pmid,month,shorttitle,keywords
\end{verbatim}

The citations are done using the normal markdown syntax, where
\texttt{@Elton1927AniEco} produces Elton (1927), and
\texttt{{[}@Camerano1880EquViv{]}} produces (Camerano 1880).

\hypertarget{figures-tables-and-other-floats}{%
\section{Figures, Tables, and other
floats}\label{figures-tables-and-other-floats}}

Note that you can wrap the text of legends for both figures and tables.
This avoids the issue of having very long lines.

\hypertarget{mathematics}{%
\subsection{Mathematics}\label{mathematics}}

The following equation

\begin{equation}\protect\hypertarget{eq:eq1}{}{J'(p) = \frac{1}{\text{log}(S)}\times\left(-\sum p \times \text{log}(p)\right)}\label{eq:eq1}\end{equation}

is produced using

\begin{Shaded}
\begin{Highlighting}[]
\SpecialStringTok{$$J\textquotesingle{}(p) = }\SpecialCharTok{\textbackslash{}frac}\SpecialStringTok{\{1\}\{}\SpecialCharTok{\textbackslash{}text}\NormalTok{\{log\}}\SpecialStringTok{(S)\}}\SpecialCharTok{\textbackslash{}times}\SpecialStringTok{ ... $$}\NormalTok{ \{\#eq:eq1\}}
\end{Highlighting}
\end{Shaded}

and can be referenced using \texttt{@eq:eq1}, which will result in
eq.~\ref{eq:eq1}. Note that because we use \texttt{pandoc-crossref}, the
label ``eq.'' will be generated automatically.

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

Table legends go on the line after the table itself. To generate a
reference to the table, use \texttt{\{\#tbl:id\}} -- then, in the text,
you can use \texttt{\{@tbl:id\}} to refer to the table. For example, the
table below is tbl.~\ref{tbl:id}. You can remove the \emph{table} in
front by using \texttt{!@tbl:id}, or force it to be capitalized with
\texttt{\textbackslash{}*tbl:id}.

\hypertarget{tbl:id}{}
\begin{longtable}[]{@{}rrrrl@{}}
\caption{\label{tbl:id}This is a table, and its identifier is
\texttt{id} -- we can refer to it using \texttt{\{@tbl:id\}}. Note that
even if the table legend is written below the table itself, it will
appear on top in the PDF document.}\tabularnewline
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
Species\tabularnewline
\midrule
\endfirsthead
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
Species\tabularnewline
\midrule
\endhead
5.1 & 3.5 & 1.4 & 0.2 & setosa\tabularnewline
5.0 & 3.6 & 1.4 & 0.2 & setosa\tabularnewline
5.4 & 3.9 & 1.7 & 0.4 & setosa\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{figures}{%
\section{Figures}\label{figures}}

Figures can have a legend -- all figures \emph{must} be in the
\texttt{figures/} folder of the project, as it is also used for the
website. We recommend to use good resolution images, rather than PDFs,
or at least to have multiple versions available.

\begin{verbatim}
![This is the legend of the figure...](figures/figure.png){#fig:figure}
\end{verbatim}

\begin{figure}
\hypertarget{fig:figure}{%
\centering
\includegraphics{figures/figure.png}
\caption{This is the legend of the figure, which will be shown in the
margin in preprint mode, and underneath the figure in draft mode. The
legend can contain references, etc. It is advised to use a resolution of
at least 600dpi for the figures.}\label{fig:figure}
}
\end{figure}

We can now use \texttt{@fig:figure} to refer to fig.~\ref{fig:figure}.

\hypertarget{example-text}{%
\section{Example text}\label{example-text}}

Connectance, defined as the ratio of realized interactions on the total
number of potential interactions, is one of the most common descriptor
of network structure. In a bipartite network with \(T\) species at the
top, and \(B\) at the bottom, having a total of \(L\) interactions, it
is defined as \(Co = L/(T\times B)\). Connectance has a lower bound, as
the network cannot have fewer interactions that the number of species in
its more speciose level -- the minimal connectance is therefore
\(c_m = \text{max}(T,B)\). This makes the connectance of networks of
different sizes difficult to compare, especially since bipartite
networks tends to have a low connectance. For this reason, we used a
corrected version of connectance, defined as

\begin{equation}\protect\hypertarget{eq:cstar}{}{Co^\star=\frac{L-c_m}{T\times B-c_m} \,.}\label{eq:cstar}\end{equation}

\hypertarget{this-is-a-subsection}{%
\subsection{This is a subsection}\label{this-is-a-subsection}}

This takes values between 0 (the network has the minimal number of
interactions) and 1 (all species are connected), but is robust to
variations in species richness.

\hypertarget{this-is-another-subsection}{%
\subsection{This is another
subsection}\label{this-is-another-subsection}}

This takes values between 0 (the network has the minimal number of
interactions) and 1 (all species are connected), but is robust to
variations in species richness.

\hypertarget{some-non-standard-maths}{%
\subsection{Some non-standard maths}\label{some-non-standard-maths}}

The phylogenetic reconstruction of \(\hat{\mathscr{L}}\) and
\(\hat{\mathscr{R}}\) has an associated uncertainty, represented by the
breadth of the uniform distribution associated to each of their entries.
Therefore, we can use this information to assemble a
\emph{probabilistic} metaweb in the sense of
(\textbf{Poisot2016StrPro?}), \emph{i.e.} in which every interaction is
represented as a single, independent, Bernoulli event of probability
\(p\).

Specifically, we have adopted the following approach. For every entry in
\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\), we draw a value from
its distribution. This results in one instance of the possible left
(\(\hat{\mathscr{l}}\)) and right (\(\hat{\mathscr{r}}\)) subspaces for
the Canadian metaweb. These can be multiplied, to produce one matrix of
real values. Because the entries in \(\hat{\mathscr{l}}\) and
\(\hat{\mathscr{r}}\) are in the same space where \(\mathscr{L}\) and
\(\mathscr{R}\) were originally predicted, it follows that the threshold
\(\rho\) estimated for the European metaweb also applies. We use this
information to produce one random Canadian metaweb,
\(N = \hat{\mathscr{L}}\)\(\hat{\mathscr{R}}' \ge \rho\).

Because the intervals around some trait values can be broad (in fact,
probably broader than what they would actually be, see \emph{e.g.}
\textbf{Garland1999IntPhy?}), we repeat the above process
\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
where the probability of an interaction (here conveying our degree of
trust that it exists given the inferred trait distributions) is given by
the number of times where it appears across all random draws \(N\),
divided by the number of samples. An interaction with \(P_{i,j} = 1\)
means that these two species were predicted to interact in all
\(2\times 10^5\) random draws, etc..

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Camerano1880EquViv}{}%
Camerano, L. (1880). Dell'equilibrio dei viventi merce la reciproca
distruzione. \emph{Atti Della R. Accad. Delle Sci. Torino}, 15,
393--414.

\leavevmode\hypertarget{ref-Elton1927AniEco}{}%
Elton, C.S. (1927). \emph{Animal ecology}. University of Chicago Press.

\end{CSLReferences}

\end{document}

### 2022-01-01 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@ce51707d1363e9cdf30f88cfc0ba3fb1ace6a007 🚀

--- 2022-01-01 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
 
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\geometry{includemp,
+            letterpaper,
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
+
+\usepackage[singlelinecheck=off]{caption}
+
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
+\setcounter{secnumdepth}{5}
 
-\doublespacing
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
-\vskip 5em
+\pagestyle{normal}
+\thispagestyle{firstpage}
 
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
+manuscripts using markdown and github actions}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 \,\textsuperscript{1,2}
-
-\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences
-
+\vskip 1em
+\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
+Centre for Biodiversity Sciences\\
+\vskip 1em
 \textbf{Correspondance to:}\\
 Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
+}
+\end{flushleft}
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
 
-\clearpage
-\thispagestyle{empty}
-
-\vfill
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+pandoc\\pandoc-crossref\\github actions\\}
+}
 
@@
 
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2022-01-01 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@13fa3e6567512b895e602da84efde7663c6d563f 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
+{\Large\bfseries\sffamily NeutralLandscapes.jl: a library for efficient
+generation of neutral landscapes with temporal change}
 \vskip 5em
@@
 \vfill
-
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+Soon to be a paper, maybe. TK authors, MKB,VB,RS,TP
 
@@
 
-This template uses \texttt{pandoc} (and a few additional python glue
-scripts) to facilitate the production of scientific articles using a
-standard markdown file. The objective is to ensure that standard
-markdown (with the important exception of the \texttt{pandoc-crossref}
-citation markup) will be rendered into an interactive website (which
-allows collaborative annotations with the \texttt{hypothes.is}
-platform), a ``draft'' style PDF (double-spaced, numbered lines, figures
-at the end), and a ``preprint'' style PDF (with slightly more
-reader-friendly pagination).
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-The core bit of configuration is the \texttt{metadata.json} file, which
-handles information about authorship, affiliations, the abstract,
-keywords, etc. All documents will be deployed to \texttt{gh-pages}
-\emph{only} on push events from the \texttt{main} branch. All of the
-artifacts will be built when doing pull requests, so you can check that
-merging a branch is \emph{not} going to cause the compilation of the
-documents to fail; indeed, you can download the artifacts produced
-during the run, to check the PDF and html files. The website is only
-updated from the \texttt{main} branch.
+Neutral landscapes are increasingly used in ecological and evolutionary
+studies over space to provide a null expectation .
 
-The workflow is \emph{very} GitHub based, and so the manuscript file
-\emph{is} the \texttt{README.md} - this is not going to be a huge issue
-as 90\% of the markdown is standard, with the exception of the citations
-and mathematics, so this will render (mostly) like a normal README file.
+As biodiversity science becomes increasingly concerned with temporal
+change and its consequences, its clear there is a gap generating neutral
+landscapes that change over time. In this ms we present how
+\texttt{NeutralLandscapes.jl} is orders of magnitudes faster than
+packages \texttt{nlmpy} (in python) or \texttt{NLMR} (in R). We then
+present a novel method for generating landscape change with prescribed
+levels of spatial and temporal autocorrelation, and demonstrate that it
+works
 
-\hypertarget{deploying-the-template}{%
-\section{Deploying the template}\label{deploying-the-template}}
+\hypertarget{software-overview}{%
+\section{Software Overview}\label{software-overview}}
 
-The process of deploying this template has been \emph{greatly}
-streamlined from previous versions:
+\textbf{Fig 1}: Recreation of the figure in \texttt{nlmpy} paper and the
+source
 
-\begin{itemize}
-\tightlist
-\item
-  Click on the ``Use this template'' button
-\item
-  Edit \texttt{README.md} with your own text, commit, and push
-\item
-  This push will trigger the first build - the builds are only active on
-  the \texttt{main} branch (\emph{not} \texttt{master}!), and on pull
-  requests
-\item
-  Go to \texttt{http://you.github.io/repo-name/} to view the html
-  version, and get access to the PDFs
-\item
-  Add your references to the \texttt{references.bib} file
-\item
-  Edit the \texttt{metadata.json} file to add the title, abstract,
-  authors
-\end{itemize}
+\hypertarget{comparison-to-nlmpy-and-nlmr}{%
+\section{\texorpdfstring{Comparison to \texttt{nlmpy} and
+\texttt{NLMR}}{Comparison to nlmpy and NLMR}}\label{comparison-to-nlmpy-and-nlmr}}
 
-In particular, note that \emph{you do not need} to create a personnal
-access token to deploy to \texttt{gh-pages} (from where the website is
-served).
+\textbf{Fig 2}: Benchmark comparison of all of methods in each of the
+three languages
 
-\hypertarget{the-metadata-file}{%
-\section{The metadata file}\label{the-metadata-file}}
+\hypertarget{generating-dynamic-neutral-landscapes}{%
+\section{Generating dynamic neutral
+landscapes}\label{generating-dynamic-neutral-landscapes}}
 
-\hypertarget{general-information}{%
-\subsection{General information}\label{general-information}}
-
-The title is a field in the \texttt{metadata.json}:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{\{}
-    \DataTypeTok{"title"}\FunctionTok{:} \StringTok{"Preprint template"}
-\FunctionTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{authorship}{%
-\subsection{Authorship}\label{authorship}}
-
-Authors are listed as objects in the \texttt{authors} block. Each author
-is specified as follows:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{\{}
-      \DataTypeTok{"familyname"}\FunctionTok{:} \StringTok{"Bob"}\FunctionTok{,}
-      \DataTypeTok{"givennames"}\FunctionTok{:} \StringTok{"Alice"}\FunctionTok{,}
-      \DataTypeTok{"email"}\FunctionTok{:} \StringTok{"alice.bob@u.edu"}\FunctionTok{,}
-      \DataTypeTok{"orcid"}\FunctionTok{:} \StringTok{"0000{-}0000{-}0000{-}0001"}\FunctionTok{,}
-      \DataTypeTok{"affiliations"}\FunctionTok{:} \OtherTok{[}
-        \StringTok{"Affiliation 1"}\OtherTok{,}
-        \StringTok{"Affiliation 2"}
-      \OtherTok{]}\FunctionTok{,}
-      \DataTypeTok{"status"}\FunctionTok{:} \OtherTok{[}\StringTok{"corresponding"}\OtherTok{,} \StringTok{"equal"}\OtherTok{]}
-    \FunctionTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-The \texttt{email} field is recommended for all authors. The
-\texttt{status} field is only useful for the corresponding author, and
-to denote equal contributions. These informations are rendered on the
-initial page. If an \texttt{orcid} is given, it will be linked on the
-HTML and PDF versions.
-
-Note that there is \emph{no need} to number the affiliations - a small
-python script will take care of this automatically.
-
-\hypertarget{abstract}{%
-\subsection{Abstract}\label{abstract}}
-
-This template supports three types of abstracts, indicated in the
-metadata file as \texttt{abstract}:
-
-A regular \texttt{abstract} is defined as
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\ErrorTok{"abstract":} \ErrorTok{"A} \ErrorTok{very} \ErrorTok{long} \ErrorTok{string"}
-\end{Highlighting}
-\end{Shaded}
-
-An itemized abstract is an array of strings, each representing a bullet
-point:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\ErrorTok{"abstract":} \OtherTok{[}
-    \StringTok{"Point 1"}\OtherTok{,}
-    \StringTok{"Point 2"}
-\OtherTok{]}
-\end{Highlighting}
-\end{Shaded}
-
-A structured abstract is an object with key-value pairs :
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\ErrorTok{"abstract":} \FunctionTok{\{}
-    \DataTypeTok{"Location"}\FunctionTok{:} \StringTok{"Worldwide"}\FunctionTok{,}
-    \DataTypeTok{"Organisms"}\FunctionTok{:} \StringTok{"Mammals"}
-\FunctionTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{citation-style}{%
-\subsection{Citation style}\label{citation-style}}
-
-The \texttt{citationstyle} key corresponds to the name, with
-\texttt{.csl} ommited, of a CSL stylesheet stored in the
-\href{https://github.com/citation-style-language/}{citation style
-language} repository. Note that there is no difference between main and
-dependent styles, the build engine will take the correct steps to get
-the correct style. The default is
-\texttt{"citationstyle":\ "ecology-letters"}. There is a longer section
-about references management later on.
-
-\hypertarget{references-management}{%
-\section{References management}\label{references-management}}
-
-The references are managed by \texttt{pandoc}. Note that we \emph{do
-not} use \texttt{pandoc-citeproc}, which was an external module for
-older \texttt{pandoc} versions. References \emph{must} be stored in a
-\texttt{references.bib} file, and that it would make sense to order it
-alphabetically by key.
-
-We use \href{https://www.zotero.org/}{Zotero} for references management,
-and for the lab's manuscripts, we work from folders in a shared library
-(with a folder for every manuscript).
-
-It is recommedned to use the
-\href{https://retorque.re/zotero-better-bibtex/}{Better BibTeX} plugin
-for citation key generations, and auto-export of the shared library to
-the \texttt{references.bib} file. We use a citation key format meant to
-convey information on the author (first author full name), date (complet
-year), and title (first three letters of the first two non-stop words).
-It must be set in the Better BibTeX preferences as (you might need to
-remove the line changes):
-
-\begin{verbatim}
-[auth:fold]
-[year]
-[title:fold:nopunctordash:skipwords:lower:select=1,1:substring=1,3:capitalize]
-[title:fold:nopunctordash:skipwords:lower:select=2,2:substring=1,3:capitalize]
-\end{verbatim}
-
-It is a good idea to configure Better BibTeX to auto-export on change,
-and to remove a lot of fields that are not strictly speaking required
-for references. The list of fields we usually ignore is:
-
-\begin{verbatim}
-abstract,copyright,annotation,file,pmid,month,shorttitle,keywords
-\end{verbatim}
-
-The citations are done using the normal markdown syntax, where
-\texttt{@Elton1927AniEco} produces Elton (1927), and
-\texttt{{[}@Camerano1880EquViv{]}} produces (Camerano 1880).
-
-\hypertarget{figures-tables-and-other-floats}{%
-\section{Figures, Tables, and other
-floats}\label{figures-tables-and-other-floats}}
-
-Note that you can wrap the text of legends for both figures and tables.
-This avoids the issue of having very long lines.
-
-\hypertarget{mathematics}{%
-\subsection{Mathematics}\label{mathematics}}
-
-The following equation
-
-\begin{equation}\protect\hypertarget{eq:eq1}{}{J'(p) = \frac{1}{\text{log}(S)}\times\left(-\sum p \times \text{log}(p)\right)}\label{eq:eq1}\end{equation}
-
-is produced using
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\SpecialStringTok{$$J\textquotesingle{}(p) = }\SpecialCharTok{\textbackslash{}frac}\SpecialStringTok{\{1\}\{}\SpecialCharTok{\textbackslash{}text}\NormalTok{\{log\}}\SpecialStringTok{(S)\}}\SpecialCharTok{\textbackslash{}times}\SpecialStringTok{ ...
-$$}\NormalTok{ \{\#eq:eq1\}}
-\end{Highlighting}
-\end{Shaded}
-
-and can be referenced using \texttt{@eq:eq1}, which will result in
-eq.~\ref{eq:eq1}. Note that because we use \texttt{pandoc-crossref}, the
-label ``eq.'' will be generated automatically.
-
-\hypertarget{tables}{%
-\subsection{Tables}\label{tables}}
-
-Table legends go on the line after the table itself. To generate a
-reference to the table, use \texttt{\{\#tbl:id\}} -- then, in the text,
-you can use \texttt{\{@tbl:id\}} to refer to the table. For example, the
-table below is tbl.~\ref{tbl:id}. You can remove the \emph{table} in
-front by using \texttt{!@tbl:id}, or force it to be capitalized with
-\texttt{\textbackslash{}*tbl:id}.
-
-\hypertarget{tbl:id}{}
-\begin{longtable}[]{@{}rrrrl@{}}
-\caption{\label{tbl:id}This is a table, and its identifier is
-\texttt{id} -- we can refer to it using \texttt{\{@tbl:id\}}. Note that
-even if the table legend is written below the table itself, it will
-appear on top in the PDF document.}\tabularnewline
-\toprule
-Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
-Species\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
-Species\tabularnewline
-\midrule
-\endhead
-5.1 & 3.5 & 1.4 & 0.2 & setosa\tabularnewline
-5.0 & 3.6 & 1.4 & 0.2 & setosa\tabularnewline
-5.4 & 3.9 & 1.7 & 0.4 & setosa\tabularnewline
-\bottomrule
-\end{longtable}
-
-\hypertarget{figures}{%
-\section{Figures}\label{figures}}
-
-Figures can have a legend -- all figures \emph{must} be in the
-\texttt{figures/} folder of the project, as it is also used for the
-website. We recommend to use good resolution images, rather than PDFs,
-or at least to have multiple versions available.
-
-\begin{verbatim}
-![This is the legend of the figure...](figures/figure.png){#fig:figure}
-\end{verbatim}
-
-\begin{figure}
-\hypertarget{fig:figure}{%
-\centering
-\includegraphics{figures/figure.png}
-\caption{This is the legend of the figure, which will be shown in the
-margin in preprint mode, and underneath the figure in draft mode. The
-legend can contain references, etc. It is advised to use a resolution of
-at least 600dpi for the figures.}\label{fig:figure}
-}
-\end{figure}
-
-We can now use \texttt{@fig:figure} to refer to fig.~\ref{fig:figure}.
-
-\hypertarget{example-text}{%
-\section{Example text}\label{example-text}}
-
-Connectance, defined as the ratio of realized interactions on the total
-number of potential interactions, is one of the most common descriptor
-of network structure. In a bipartite network with \(T\) species at the
-top, and \(B\) at the bottom, having a total of \(L\) interactions, it
-is defined as \(Co = L/(T\times B)\). Connectance has a lower bound, as
-the network cannot have fewer interactions that the number of species in
-its more speciose level -- the minimal connectance is therefore
-\(c_m = \text{max}(T,B)\). This makes the connectance of networks of
-different sizes difficult to compare, especially since bipartite
-networks tends to have a low connectance. For this reason, we used a
-corrected version of connectance, defined as
-
-\begin{equation}\protect\hypertarget{eq:cstar}{}{Co^\star=\frac{L-c_m}{T\times B-c_m} \,.}\label{eq:cstar}\end{equation}
-
-\hypertarget{this-is-a-subsection}{%
-\subsection{This is a subsection}\label{this-is-a-subsection}}
-
-This takes values between 0 (the network has the minimal number of
-interactions) and 1 (all species are connected), but is robust to
-variations in species richness.
-
-\hypertarget{this-is-another-subsection}{%
-\subsection{This is another
-subsection}\label{this-is-another-subsection}}
-
-This takes values between 0 (the network has the minimal number of
-interactions) and 1 (all species are connected), but is robust to
-variations in species richness.
-
-\hypertarget{some-non-standard-maths}{%
-\subsection{Some non-standard maths}\label{some-non-standard-maths}}
-
-The phylogenetic reconstruction of \(\hat{\mathscr{L}}\) and
-\(\hat{\mathscr{R}}\) has an associated uncertainty, represented by the
-breadth of the uniform distribution associated to each of their entries.
-Therefore, we can use this information to assemble a
-\emph{probabilistic} metaweb in the sense of
-(\textbf{Poisot2016StrPro?}), \emph{i.e.} in which every interaction is
-represented as a single, independent, Bernoulli event of probability
-\(p\).
-
-Specifically, we have adopted the following approach. For every entry in
-\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\), we draw a value from
-its distribution. This results in one instance of the possible left
-(\(\hat{\mathscr{l}}\)) and right (\(\hat{\mathscr{r}}\)) subspaces for
-the Canadian metaweb. These can be multiplied, to produce one matrix of
-real values. Because the entries in \(\hat{\mathscr{l}}\) and
-\(\hat{\mathscr{r}}\) are in the same space where \(\mathscr{L}\) and
-\(\mathscr{R}\) were originally predicted, it follows that the threshold
-\(\rho\) estimated for the European metaweb also applies. We use this
-information to produce one random Canadian metaweb,
-\(N = \hat{\mathscr{L}}\)\(\hat{\mathscr{R}}' \ge \rho\).
-
-Because the intervals around some trait values can be broad (in fact,
-probably broader than what they would actually be, see \emph{e.g.}
-\textbf{Garland1999IntPhy?}), we repeat the above process
-\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
-where the probability of an interaction (here conveying our degree of
-trust that it exists given the inferred trait distributions) is given by
-the number of times where it appears across all random draws \(N\),
-divided by the number of samples. An interaction with \(P_{i,j} = 1\)
-means that these two species were predicted to interact in all
-\(2\times 10^5\) random draws, etc..
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
 \hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Camerano1880EquViv}{}%
-Camerano, L. (1880). Dell'equilibrio dei viventi merce la reciproca
-distruzione. \emph{Atti Della R. Accad. Delle Sci. Torino}, 15,
-393--414.
-
-\leavevmode\hypertarget{ref-Elton1927AniEco}{}%
-Elton, C.S. (1927). \emph{Animal ecology}. University of Chicago Press.
-
-\end{CSLReferences}
+\section{References}\label{references}}
 

### 2022-01-01 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@13fa3e6567512b895e602da84efde7663c6d563f 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
-manuscripts using markdown and github actions}}}
+\noindent {\LARGE \textbf{\textsf{NeutralLandscapes.jl: a library for
+efficient generation of neutral landscapes with temporal change}}}
 
@@
 {\small{\bfseries Keywords}:\par
-pandoc\\pandoc-crossref\\github actions\\}
+landscape ecology\\spatial ecology\\neutral landscapes\\simulation\\}
 }
 
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+Soon to be a paper, maybe. TK authors, MKB,VB,RS,TP
 

### 2022-01-01 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@712a8befa336a6cc3f43b1c5041e1deb3e9fe107 🚀

@@
 
-\textbf{Fig 1}: Recreation of the figure in \texttt{nlmpy} paper and the
-source
+This software can generate neutral landscapes using twenty different
+methods.
 
-\hypertarget{comparison-to-nlmpy-and-nlmr}{%
-\section{\texorpdfstring{Comparison to \texttt{nlmpy} and
-\texttt{NLMR}}{Comparison to nlmpy and NLMR}}\label{comparison-to-nlmpy-and-nlmr}}
+fig.~\ref{fig:allmethods} shows a replica of Figure 1 from
+(\textbf{nlmpycite?})
+
+Table of methods.
+
+\begin{figure}
+\hypertarget{fig:allmethods}{%
+\centering
+\includegraphics{./figures/figure1.png}
+\caption{Recreation of the figure in \texttt{nlmpy} paper and the
+source}\label{fig:allmethods}
+}
+\end{figure}
+
+\begin{verbatim}
+using NeutralLandscapes, Plots
+siz = 50, 50
+
+Fig1a = rand(NoGradient(), siz) # Random NLM
+Fig1b = rand(PlanarGradient(), siz) # Planar gradient NLM
+Fig1c = rand(EdgeGradient(), siz) # Edge gradient NLM
+Fig1d = falses(siz) 
+Fig1d[10:25, 10:25] .= true # Mask example
+Fig1e = rand(DistanceGradient(findall(vec(Fig1d))), siz) # Mask example
+Fig1f = rand(MidpointDisplacement(0.75), siz) # Mask example
+Fig1g = rand(RectangularCluster(4, 8), siz)
+Fig1h = rand(NearestNeighborElement(200), siz)
+Fig1i = rand(NearestNeighborCluster(0.4), siz)
+Fig1j = blend([Fig1f, Fig1c])
+Fig1k = blend(Fig1h, Fig1e, 1.5)
+Fig1l = classify(Fig1i, ones(4))
+Fig1m = classify(Fig1a, [1-0.5, 0.5])
+Fig1n = classify(Fig1g, [1-0.75, 0.75])
+Fig1o = classify(Fig1f, ones(3))
+Fig1p = classify(Fig1f, ones(3), Fig1d)
+Fig1q = rand(PlanarGradient(90), siz, mask = Fig1n .== 2) #TODO mask as keyword + should mask be matrix or vec or both? (Fig1e)
+Fig1r = ifelse.(Fig1o .== 2, Fig1m .+ 2, Fig1o)
+Fig1s = rotr90(Fig1l)
+Fig1t = Fig1o'
+
+class = cgrad(:Set3_4, 4, categorical = true)
+c2, c3, c4 = class[1:2], class[1:3], class[1:4]
+
+gr(color = :fire, ticks = false, framestyle = :box, dpi=500, colorbar = false)
+plot(
+    heatmap(Fig1a),         heatmap(Fig1b),         heatmap(Fig1c),         heatmap(Fig1d, c = c2), heatmap(Fig1e),
+    heatmap(Fig1f),         heatmap(Fig1g),         heatmap(Fig1h),         heatmap(Fig1i),         heatmap(Fig1j), 
+    heatmap(Fig1k),         heatmap(Fig1l, c = c4), heatmap(Fig1m, c = c2), heatmap(Fig1n, c = c2), heatmap(Fig1o, c = c3),
+    heatmap(Fig1p, c = c4), heatmap(Fig1q),         heatmap(Fig1r, c = c4), heatmap(Fig1s, c = c4), heatmap(Fig1t, c = c3),
+    layout = (4,5), size = (1600, 1270)
+)
+
+savefig("./figures/figure1.png", )
+\end{verbatim}
+
+\hypertarget{benchmark-comparison-to-nlmpy-and-nlmr}{%
+\section{\texorpdfstring{Benchmark comparison to \texttt{nlmpy} and
+\texttt{NLMR}}{Benchmark comparison to nlmpy and NLMR}}\label{benchmark-comparison-to-nlmpy-and-nlmr}}
 
@@
 
+We implement methods for generating change that are temporally
+autocorrelated, spatially autocorrelated, or both.
+
+\(M_t = f(M_{t-1})\)
+
 \hypertarget{discussion}{%

### 2022-01-01 src/01_make_all_types.jl
up

@@ -1,0 +1,38 @@
+using NeutralLandscapes, Plots
+siz = 50, 50
+
+Fig1a = rand(NoGradient(), siz) # Random NLM
+Fig1b = rand(PlanarGradient(), siz) # Planar gradient NLM
+Fig1c = rand(EdgeGradient(), siz) # Edge gradient NLM
+Fig1d = falses(siz) 
+Fig1d[10:25, 10:25] .= true # Mask example
+Fig1e = rand(DistanceGradient(findall(vec(Fig1d))), siz) # Mask example
+Fig1f = rand(MidpointDisplacement(0.75), siz) # Mask example
+Fig1g = rand(RectangularCluster(4, 8), siz)
+Fig1h = rand(NearestNeighborElement(200), siz)
+Fig1i = rand(NearestNeighborCluster(0.4), siz)
+Fig1j = blend([Fig1f, Fig1c])
+Fig1k = blend(Fig1h, Fig1e, 1.5)
+Fig1l = classify(Fig1i, ones(4))
+Fig1m = classify(Fig1a, [1-0.5, 0.5])
+Fig1n = classify(Fig1g, [1-0.75, 0.75])
+Fig1o = classify(Fig1f, ones(3))
+Fig1p = classify(Fig1f, ones(3), Fig1d)
+Fig1q = rand(PlanarGradient(90), siz, mask = Fig1n .== 2) #TODO mask as keyword + should mask be matrix or vec or both? (Fig1e)
+Fig1r = ifelse.(Fig1o .== 2, Fig1m .+ 2, Fig1o)
+Fig1s = rotr90(Fig1l)
+Fig1t = Fig1o'
+
+class = cgrad(:Set3_4, 4, categorical = true)
+c2, c3, c4 = class[1:2], class[1:3], class[1:4]
+
+gr(color = :fire, ticks = false, framestyle = :box, dpi=500, colorbar = false)
+plot(
+    heatmap(Fig1a),         heatmap(Fig1b),         heatmap(Fig1c),         heatmap(Fig1d, c = c2), heatmap(Fig1e),
+    heatmap(Fig1f),         heatmap(Fig1g),         heatmap(Fig1h),         heatmap(Fig1i),         heatmap(Fig1j), 
+    heatmap(Fig1k),         heatmap(Fig1l, c = c4), heatmap(Fig1m, c = c2), heatmap(Fig1n, c = c2), heatmap(Fig1o, c = c3),
[…]

### 2022-01-01 src/03_scale_bench.jl

@@ -1,0 +1,35 @@
+using CSV, DataFrames
+using Plots
+using LaTeXStrings
+
+jl = CSV.read("src/benchmarking/juliascaling_means.csv", DataFrame)
+r = CSV.read("src/benchmarking/r_scalebench.csv", DataFrame)
+py = CSV.read("src/benchmarking/py_scalebench.csv", DataFrame)
+
+rmean = 
+pymean = 
+
+
+jl
+ugh = [L"2^3", L"2^4", L"2^5", L"2^6", L"2^7", L"2^8", L"2^9", L"2^{10}", L"2^{11}", L"2^{12}"]
+
+scatter(jl.side, jl.time_seconds,
+    label="NeutralLandscapes.jl", 
+    xlabel="Raster side length",
+    ylabel="Execution time (seconds)",
+    frame=:box,
+    grid=:scientific,
+    legend=:outerright,
+    yscale=:log10, 
+    xlim=(2.5,12.5),
+    xticks=(3:12,ugh),
+    ylim=(10^-5, 10^2),
+    dpi=300)
+plot!(jl.side, jl.time_seconds, c=:dodgerblue)
+
+scatter!(log2.(r.sidelength), (r.time_sec), 
+    label="NLMR (using C++)", 
+    ma=0.1)
+scatter!(log2.(py.size), py.time_seconds, 
+    ma=0.1,
+    label="nlmpy")

### 2022-01-01 src/benchmarking/juliabench.jl

@@ -1,0 +1,35 @@
+using NeutralLandscapes
+using BenchmarkTools
+using Plots
+using DataFrames
+ns = 1000
+siz = 250, 250
+
+
+ng = @benchmark rand(NoGradient(), siz) samples=ns
+pg = @benchmark rand(PlanarGradient(), siz) samples=ns
+eg = @benchmark rand(EdgeGradient(), siz)  samples=ns
+
+mpd = @benchmark rand(MidpointDisplacement(0.75), siz)  samples=ns
+nne = @benchmark rand(NearestNeighborElement(200), siz)  samples=ns
+nnc = @benchmark rand(NearestNeighborCluster(0.4), siz)  samples=ns
+
+mpd
+heatmap(rand(NearestNeighborCluster(0.4), siz))
+
+function scalebench()
+    df = DataFrame(side=[], meantime_ns=[])
+    for s in collect(3:13)
+        thistime = @benchmark rand(MidpointDisplacement(0.8), 2^s, 2^s) setup=(s=$s) 
+        newdf = DataFrame(side=[s], meantime_ns=[mean(thistime.times)])
+        df = [df;newdf]
+    end
+    df
+end
+
+df = scalebench()
+
+df.time_seconds = df.meantime_ns ./ 10^9
+
+using CSV
+CSV.write("juliascaling.csv",df)

### 2022-01-01 src/benchmarking/python_bench.py

@@ -1,0 +1,46 @@
+from nlmpy import nlmpy
+import time
+
+nlm = nlmpy.mpd(nRow=50, nCol=50, h=0.75)
+
+
+methods = dict(
+    r = lambda: nlmpy.random(250,250), 
+    pg = lambda: nlmpy.planarGradient(250,250), 
+    dg = lambda: nlmpy.distanceGradient(nlmpy.planarGradient(250,250)), 
+    eg = lambda: nlmpy.edgeGradient(250,250),
+    ws = lambda: nlmpy.waveSurface(250,250, 4), 
+    mpd = lambda: nlmpy.mpd(256, 256,0.8), 
+    pn = lambda: nlmpy.perlinNoise(250,250, (4,4)),
+    renn = lambda: nlmpy.randomElementNN(250,250,10), 
+    rcnn = lambda: nlmpy.randomClusterNN(250,250, 0.4),  
+)
+
+nbatches = 1000
+import csv
+"""
+with open('pybench.csv', 'w') as csvfile:
+    writer = csv.writer(csvfile)
+    writer.writerow(["method", "batch", "mean_execution_time"])
+
+    for key in methods: 
+        for batch in range(0,nbatches):
+            t1 = time.time()
+            r = methods[key]()
+            t2 = time.time()
+            writer.writerow([key, batch, t2-t1])
+"""
+            
+
+with open('py_scalebench.csv', 'w') as csvfile:
+    writer = csv.writer(csvfile)
+    writer.writerow(["size", "batch", "time_seconds"])
+    nbatches = 50
+    for sideexp in range(3, 13):
+        for batch in range(0,nbatches):
+            t1 = time.time()
+            r = nlmpy.mpd(2**sideexp,2**sideexp,0.8),
+            t2 = time.time()
+            writer.writerow([2**sideexp, batch, t2-t1])
+
+            

### 2022-01-01 src/benchmarking/rbench.R

@@ -1,0 +1,32 @@
+#install.packages("NLMR")
+#install.packages("microbenchmark")
+
+library("NLMR")
+library("microbenchmark")
+
+rand = microbenchmark(nlm_random(250,250,1), 1000)
+
+dg = nlm_distancegradient(250,250, origin=c(1,1,1,1))
+
+eg = nlm_edgegradient(250,250)
+mpd = microbenchmark(nlm_mpd(256, 256), times=1000)
+rrc = nlm_randomrectangularcluster(250,250, minl=10, maxl=150)
+
+
+#nne = nlm_neigh(250,250, p_neigh=0.1,p_empty=0)
+nnc = nlm_randomcluster(250,250, p=0.9)
+
+
+# scale dep 
+
+sideexp = seq(3,12)
+
+df = data.frame(sidelength=c(0), time_nanoseconds=c(0))
+for (s in sideexp){
+    bm = microbenchmark(nlm_mpd(2^s, 2^s), times=50)  
+    newdf = data.frame(sidelength=2^s, time_nanoseconds=mean(bm$time))
+    df = rbind(df, newdf)
+}
+
+df$time_sec = df$time_nanoseconds / 10^9
+write.csv(df, "r_scalebench.csv")

### 2022-01-01 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@ab58068f48cf349c47594dae2efced6b1f0a50fd 🚀

@@
 Neutral landscapes are increasingly used in ecological and evolutionary
-studies over space to provide a null expectation .
+studies to provide a null expectation of the variance of a given metric
+over space.
+
+Wide range of disciplines: landscape genetics to biogeography.
 
@@
 
-This software can generate neutral landscapes using twenty different
-methods.
+This software can generate neutral landscapes using several methods,
+enables masking and works with other julia packages.
 
@@
 
+\hypertarget{interoperability}{%
+\subsection{Interoperability}\label{interoperability}}
+
+Ease of use with other julia packages
+
+Mask of neutral variable masked across quebec in 3 lines.
+
 \hypertarget{benchmark-comparison-to-nlmpy-and-nlmr}{%
@@
 
-\textbf{Fig 2}: Benchmark comparison of all of methods in each of the
+It's fast. As the scale and resolution of raster data increases, neutral
+models must be able to scale to match those data dimensions.
+
+Here we provide two benchmark tests.
+
+First a comparison of the speed variety of methods from each
+\texttt{NeutralLandscapes.jl}, \texttt{NLMR}, and \texttt{nlmpy}.
+
+Second we compare these performance of each of these software packages
+as rasters become larger. We show that \texttt{Julia} even outperforms
+the \texttt{NLMR} via C++ implemention of a particularly slow neutral
+landscape method (midpoint displacement).
+
+\textbf{Fig 2}: Benchmark comparison of selected methods in each of the
 three languages
+
+\textbf{Fig 3} scale comparison
+
+\begin{figure}
+\centering
+\includegraphics{}
+\caption{Comparison of speed of generating a midpoint displacement
+neutral landscape (y-axis) against raster size (measured as length of
+the size of a square raster, x-axis)}
+\end{figure}
 

### 2022-01-01 src/03_scale_bench.jl
up

@@ -25,7 +25,7 @@ scatter(jl.side, jl.time_seconds,
     xticks=(3:12,ugh),
     ylim=(10^-5, 10^2),
     dpi=300)
-plot!(jl.side, jl.time_seconds, c=:dodgerblue)
+plot!(jl.side, jl.time_seconds, c=:dodgerblue, label="")
 
 scatter!(log2.(r.sidelength), (r.time_sec), 
     label="NLMR (using C++)", 
@@ -33,3 +33,5 @@ scatter!(log2.(r.sidelength), (r.time_sec),
 scatter!(log2.(py.size), py.time_seconds, 
     ma=0.1,
     label="nlmpy")
+
+    savefig("draftfig3.png")

### 2022-01-01 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@7d7a47946d791dcbc99a0c25675c4acea4a92c36 🚀

@@
 
-Wide range of disciplines: landscape genetics to biogeography.
+Wide range of disciplines: from landscape genetics {[}{]}, to spatial
+ecology {[}{]}, and biogeography {[}{]}.
 
@@
 \texttt{NeutralLandscapes.jl} is orders of magnitudes faster than
-packages \texttt{nlmpy} (in python) or \texttt{NLMR} (in R). We then
-present a novel method for generating landscape change with prescribed
-levels of spatial and temporal autocorrelation, and demonstrate that it
-works
+packages \texttt{nlmpy} (in python) or \texttt{NLMR} (in R). In addition
+we then present a novel method for generating landscape change with
+prescribed levels of spatial and temporal autocorrelation.
 
@@
 fig.~\ref{fig:allmethods} shows a replica of Figure 1 from
-(\textbf{nlmpycite?})
+(\textbf{nlmpycite?}), which shows the capacity of the library to
+generate different types of neutral landscapes, and then apply masks and
+categorical classifcation to them.
 
 Table of methods.
+
+In
 
@@
 \caption{Recreation of the figure in \texttt{nlmpy} paper and the
-source}\label{fig:allmethods}
+source, supplied in less than 40 lines of code.}\label{fig:allmethods}
 }
@@
 
-\begin{verbatim}
-using NeutralLandscapes, Plots
-siz = 50, 50
-
-Fig1a = rand(NoGradient(), siz) # Random NLM
-Fig1b = rand(PlanarGradient(), siz) # Planar gradient NLM
-Fig1c = rand(EdgeGradient(), siz) # Edge gradient NLM
-Fig1d = falses(siz) 
-Fig1d[10:25, 10:25] .= true # Mask example
-Fig1e = rand(DistanceGradient(findall(vec(Fig1d))), siz) # Mask example
-Fig1f = rand(MidpointDisplacement(0.75), siz) # Mask example
-Fig1g = rand(RectangularCluster(4, 8), siz)
-Fig1h = rand(NearestNeighborElement(200), siz)
-Fig1i = rand(NearestNeighborCluster(0.4), siz)
-Fig1j = blend([Fig1f, Fig1c])
-Fig1k = blend(Fig1h, Fig1e, 1.5)
-Fig1l = classify(Fig1i, ones(4))
-Fig1m = classify(Fig1a, [1-0.5, 0.5])
-Fig1n = classify(Fig1g, [1-0.75, 0.75])
-Fig1o = classify(Fig1f, ones(3))
-Fig1p = classify(Fig1f, ones(3), Fig1d)
-Fig1q = rand(PlanarGradient(90), siz, mask = Fig1n .== 2) #TODO mask as keyword + should mask be matrix or vec or both? (Fig1e)
-Fig1r = ifelse.(Fig1o .== 2, Fig1m .+ 2, Fig1o)
-Fig1s = rotr90(Fig1l)
-Fig1t = Fig1o'
-
-class = cgrad(:Set3_4, 4, categorical = true)
-c2, c3, c4 = class[1:2], class[1:3], class[1:4]
-
-gr(color = :fire, ticks = false, framestyle = :box, dpi=500, colorbar = false)
-plot(
-    heatmap(Fig1a),         heatmap(Fig1b),         heatmap(Fig1c),         heatmap(Fig1d, c = c2), heatmap(Fig1e),
-    heatmap(Fig1f),         heatmap(Fig1g),         heatmap(Fig1h),         heatmap(Fig1i),         heatmap(Fig1j), 
-    heatmap(Fig1k),         heatmap(Fig1l, c = c4), heatmap(Fig1m, c = c2), heatmap(Fig1n, c = c2), heatmap(Fig1o, c = c3),
-    heatmap(Fig1p, c = c4), heatmap(Fig1q),         heatmap(Fig1r, c = c4), heatmap(Fig1s, c = c4), heatmap(Fig1t, c = c3),
-    layout = (4,5), size = (1600, 1270)
-)
-
-savefig("./figures/figure1.png", )
-\end{verbatim}
+\hypertarget{what-methods-have-been-called-different-things-but-are-actually-the-same-thing}{%
+\subsection{What methods have been called different things but are
+actually the same
+thing?}\label{what-methods-have-been-called-different-things-but-are-actually-the-same-thing}}
 
@@
 It's fast. As the scale and resolution of raster data increases, neutral
-models must be able to scale to match those data dimensions.
-
-Here we provide two benchmark tests.
-
-First a comparison of the speed variety of methods from each
-\texttt{NeutralLandscapes.jl}, \texttt{NLMR}, and \texttt{nlmpy}.
-
-Second we compare these performance of each of these software packages
-as rasters become larger. We show that \texttt{Julia} even outperforms
-the \texttt{NLMR} via C++ implemention of a particularly slow neutral
-landscape method (midpoint displacement).
+models must be able to scale to match those data dimensions. Here we
+provide two benchmark tests. First a comparison of the speed variety of
+methods from each \texttt{NeutralLandscapes.jl}, \texttt{NLMR}, and
+\texttt{nlmpy}. Second we compare these performance of each of these
+software packages as rasters become larger. We show that \texttt{Julia}
+even outperforms the \texttt{NLMR} via C++ implemention of a
+particularly slow neutral landscape method (midpoint displacement).
 
@@
 
-\textbf{Fig 3} scale comparison
+In fig 2 we should a selection of neutral landscape generators (random,
+edge gradient, perlin noise, distance-gradient)
+
+\hypertarget{mpd-comparison}{%
+\subsection{MPD comparison}\label{mpd-comparison}}
+
+Why use this particular generator as the comparison? It's slow. So slow
+that NLMR implements it in C++. (NLMR implements both MPD, neighbor,
+randrect, and random neighboorhood in c++). Still these three
+algorithms, which cosinsts of 3/16 of NLMR's alg implementations,
+constitute 33\% of its codebase.
+
+In this section we show our implementation of MPD is faster than NLMR's
+C++ MPD across all scales, up to the asyptotic limit imposed by the
+\(O(n^2)\) scaling of the raster
 
@@
 \centering
-\includegraphics{}
+\includegraphics{./figures/draftfig3.png}
 \caption{Comparison of speed of generating a midpoint displacement

### 2022-01-02 src/03_scale_bench.jl
update

@@ -1,37 +1,59 @@
 using CSV, DataFrames
+using DataFramesMeta
 using Plots
 using LaTeXStrings
+using Unitful: mm
 
 jl = CSV.read("src/benchmarking/juliascaling_means.csv", DataFrame)
 r = CSV.read("src/benchmarking/r_scalebench.csv", DataFrame)
 py = CSV.read("src/benchmarking/py_scalebench.csv", DataFrame)
 
-rmean = 
-pymean = 
+rgrp = groupby(r, :sidelength)
+rmean = @combine(rgrp, :time = mean(:time_sec))
+
+pygrp = groupby(py, :size)
+pymean = @combine(pygrp, :time = mean(:time_seconds))
 
 
 jl
 ugh = [L"2^3", L"2^4", L"2^5", L"2^6", L"2^7", L"2^8", L"2^9", L"2^{10}", L"2^{11}", L"2^{12}"]
 
-scatter(jl.side, jl.time_seconds,
-    label="NeutralLandscapes.jl", 
+ylab = [L"10^{-5}",L"10^{-4}",L"10^{-3}",L"10^{-2}",L"10^{-1}",L"10^{0}", L"10^{1}", L"10^{2}",  ]
+
+plot(jl.side, jl.time_seconds, lw=1.5,lc=:dodgerblue,    label="NeutralLandscapes.jl")
+scatter!(jl.side, jl.time_seconds,
+    label="",
+    fontfamily = "computer modern",
     xlabel="Raster side length",
     ylabel="Execution time (seconds)",
     frame=:box,
     grid=:scientific,
     legend=:outerright,
+    tickfontsize=10,
+    mc=:white,
+    msw=2,
+    ms=4,
+    ma=0.9,
+    msc=:dodgerblue,
     yscale=:log10, 
-    xlim=(2.5,12.5),
+    xlim=(3,12.1),
+    yticks=([10.0^i for i in -5:2], ylab),
     xticks=(3:12,ugh),
-    ylim=(10^-5, 10^2),
-    dpi=300)
-plot!(jl.side, jl.time_seconds, c=:dodgerblue, label="")
+    ylim=(10^-5, 10^1),
+    dpi=500,
+    size=(700, 450))
 
-scatter!(log2.(r.sidelength), (r.time_sec), 
-    label="NLMR (using C++)", 
-    ma=0.1)
-scatter!(log2.(py.size), py.time_seconds, 
-    ma=0.1,
-    label="nlmpy")
 
[…]

### 2022-01-02 src/benchmarking/python_bench.py

@@ -36,7 +36,7 @@ with open('py_scalebench.csv', 'w') as csvfile:
     writer = csv.writer(csvfile)
     writer.writerow(["size", "batch", "time_seconds"])
     nbatches = 50
-    for sideexp in range(3, 13):
+    for sideexp in range(3, 11):
         for batch in range(0,nbatches):
             t1 = time.time()
             r = nlmpy.mpd(2**sideexp,2**sideexp,0.8),

### 2022-01-02 src/benchmarking/rbench.R

@@ -19,7 +19,7 @@ nnc = nlm_randomcluster(250,250, p=0.9)
 
 # scale dep 
 
-sideexp = seq(3,12)
+sideexp = seq(3,13)
 
 df = data.frame(sidelength=c(0), time_nanoseconds=c(0))
 for (s in sideexp){
@@ -30,3 +30,6 @@ for (s in sideexp){
 
 df$time_sec = df$time_nanoseconds / 10^9
 write.csv(df, "r_scalebench.csv")
+
+
+

### 2022-01-02 src/02_differentmodels_bench.jl
up

@@ -1,0 +1,116 @@
+using DataFrames, CSV, DataFramesMeta
+using Plots
+
+
+jl = CSV.read("src/benchmarking/juliabench_differentmodels.csv", DataFrame)
+r = CSV.read("src/benchmarking/rbench_differentmodels.csv", DataFrame)
+py = CSV.read("src/benchmarking/pybench_differentmodels.csv", DataFrame)
+
+r.time = r.time_nanoseconds ./ 10^9
+jl.time = jl.time_nanoseconds ./ 10^9
+py.time = py.mean_execution_time
+
+
+jlsets = (label="", mc=:dodgerblue, ma=0.01)
+rsets = (label="", mc=:mediumpurple, ma=0.01)
+pysets = (label="", mc=:green, ma=0.01)
+
+plot(xlim=(0,7), dpi=300, size=(600,300), frame=:box, legend=:outerright, yscale=:log10, xrotation=-90, ylim=(10^-3.5, 0.1), xticks=(0:7, ["", "random", "edge gradient", "planar grad", "NNE", "NNC","Perlin Noise"]))
+
+jl_random = filter(r->r.model=="random", jl) |> DataFrame
+py_random = filter(r->r.method=="random", py) |> DataFrame
+r_random = filter(r->r.model=="random", r) |> DataFrame
+scatter!(
+    [1 for i in 1:length(jl_random.time)] .- 0.2rand(1000), 
+    jl_random.time_nanoseconds ./ 10^9,
+    ;jlsets...)
+
+scatter!(
+    [1 for i in 1:length(r_random.time)] .- 0.1.-0.2rand(1000),  
+    r_random.time_nanoseconds ./ 10^9,
+    ; rsets...)
+
+scatter!(
+    [1 for i in 1:length(jl_random.time_nanoseconds)] .+ 0.2rand(1000), 
+    py_random.time,
+    ; pysets...)
+
+jl_eg = filter(r->r.model=="edge gradient", jl) |> DataFrame
+py_eg = filter(r->r.method=="eg", py) |> DataFrame
+r_eg = filter(r->r.model=="edge gradient", r) |> DataFrame
+scatter!(
+    [2 for i in 1:length(jl_random.time_nanoseconds)] .+ 0.2rand(1000), 
+    jl_eg.time ,
+    ; jlsets...)
+scatter!(
[…]

### 2022-01-02 src/benchmarking/juliabench.jl

@@ -1,21 +1,44 @@
 using NeutralLandscapes
 using BenchmarkTools
 using Plots
-using DataFrames
+using DataFrames, CSV
 ns = 1000
 siz = 250, 250
 
 
-ng = @benchmark rand(NoGradient(), siz) samples=ns
 pg = @benchmark rand(PlanarGradient(), siz) samples=ns
 eg = @benchmark rand(EdgeGradient(), siz)  samples=ns
-
+random = @benchmark rand(NoGradient(), siz)  samples=ns
 mpd = @benchmark rand(MidpointDisplacement(0.75), siz)  samples=ns
-nne = @benchmark rand(NearestNeighborElement(200), siz)  samples=ns
+nne = @benchmark rand(NearestNeighborElement(10), siz)  samples=ns
 nnc = @benchmark rand(NearestNeighborCluster(0.4), siz)  samples=ns
+rect = @benchmark rand(RectangularCluster(10,150), siz) samples=ns
+perlin = @benchmark rand(PerlinNoise((4,4)), siz) samples=ns
 
-mpd
-heatmap(rand(NearestNeighborCluster(0.4), siz))
+
+
+pg, eg, random, mpd, nne, rect
+
+pgdf = DataFrame(model=["planar gradient" for i in 1:length(pg.times)], time_nanoseconds=pg.times)
+egdf = DataFrame(model=["edge gradient" for i in 1:length(eg.times)], time_nanoseconds=eg.times)
+randomdf = DataFrame(model=["random" for i in 1:length(random.times)], time_nanoseconds=random.times)
+mpddf = DataFrame(model=["midpoint displacement" for i in 1:length(mpd.times)], time_nanoseconds=mpd.times)
+nnedf = DataFrame(model=["nearest neighbor element" for i in 1:length(nne.times)], time_nanoseconds=nne.times)
+nncdf = DataFrame(model=["nearest neighbor cluster" for i in 1:length(nnc.times)], time_nanoseconds=nnc.times)
+perlindf = DataFrame(model=["perlin" for i in 1:length(perlin.times)], time_nanoseconds=perlin.times)
+
+df = [pgdf;egdf;randomdf;mpddf;nnedf;nncdf;perlindf]
+
+CSV.write("juliabench_differentmodels.csv", df)
+
+
+
+
+
+
+
+
+
 
 function scalebench()
     df = DataFrame(side=[], meantime_ns=[])

### 2022-01-02 src/benchmarking/python_bench.py

@@ -5,20 +5,19 @@ nlm = nlmpy.mpd(nRow=50, nCol=50, h=0.75)
 
 
 methods = dict(
-    r = lambda: nlmpy.random(250,250), 
+    random = lambda: nlmpy.random(250,250), 
     pg = lambda: nlmpy.planarGradient(250,250), 
     dg = lambda: nlmpy.distanceGradient(nlmpy.planarGradient(250,250)), 
     eg = lambda: nlmpy.edgeGradient(250,250),
     ws = lambda: nlmpy.waveSurface(250,250, 4), 
-    mpd = lambda: nlmpy.mpd(256, 256,0.8), 
-    pn = lambda: nlmpy.perlinNoise(250,250, (4,4)),
+    mpd = lambda: nlmpy.mpd(256,256,0.8), 
+    perlin = lambda: nlmpy.perlinNoise(250,250, (2,2)),
     renn = lambda: nlmpy.randomElementNN(250,250,10), 
     rcnn = lambda: nlmpy.randomClusterNN(250,250, 0.4),  
 )
 
 nbatches = 1000
 import csv
-"""
 with open('pybench.csv', 'w') as csvfile:
     writer = csv.writer(csvfile)
     writer.writerow(["method", "batch", "mean_execution_time"])
@@ -29,9 +28,9 @@ with open('pybench.csv', 'w') as csvfile:
             r = methods[key]()
             t2 = time.time()
             writer.writerow([key, batch, t2-t1])
-"""
-            
 
+            
+"""
 with open('py_scalebench.csv', 'w') as csvfile:
     writer = csv.writer(csvfile)
     writer.writerow(["size", "batch", "time_seconds"])
@@ -44,3 +43,4 @@ with open('py_scalebench.csv', 'w') as csvfile:
             writer.writerow([2**sideexp, batch, t2-t1])
 
             
+"""

### 2022-01-02 src/benchmarking/rbench.R

@@ -4,18 +4,35 @@
 library("NLMR")
 library("microbenchmark")
 
-rand = microbenchmark(nlm_random(250,250,1), 1000)
-
-dg = nlm_distancegradient(250,250, origin=c(1,1,1,1))
-
-eg = nlm_edgegradient(250,250)
+rand = microbenchmark(nlm_random(250,250,1), times=1000)
+dg = microbenchmark(nlm_distancegradient(250,250, origin=c(1,1,1,1)), times=1000)
+eg = microbenchmark(nlm_edgegradient(250,250), times=1000)
 mpd = microbenchmark(nlm_mpd(256, 256), times=1000)
-rrc = nlm_randomrectangularcluster(250,250, minl=10, maxl=150)
+rrc = microbenchmark(nlm_randomrectangularcluster(250,250, minl=10, maxl=150), times=1000)
+nne = microbenchmark(nlm_mosaictess(250,250,germs=10),times=1000)
+#nnc = microbenchmark(nlm_randomcluster(250,250, p=0.4),times=1000)
 
+df = data.frame(matrix(nrow=1,ncol=3))
+colnames(df) = c("model", "replicate", "time_nanoseconds")
 
-#nne = nlm_neigh(250,250, p_neigh=0.1,p_empty=0)
-nnc = nlm_randomcluster(250,250, p=0.9)
+makedf = function(df, modeldf, name){
+    newdf = data.frame(matrix(nrow=1000,ncol=3))
+    colnames(newdf) = c("model", "replicate", "time_nanoseconds")
 
+    newdf$model = rep(name, 1000)
+    newdf$replicate = seq(1,1000)
+    newdf$time_nanoseconds = modeldf$time
+    return(rbind(df, newdf))
+}
+
+df = makedf(df, rand, "random")
+df = makedf(df, dg, "distance gradient")
+df = makedf(df, eg, "edge gradient")
+df = makedf(df, mpd, "midpoint displacement")
+df = makedf(df, rrc, "rectangle cluster")
+df = makedf(df, nne, "nearest neighbor element")
+
+write.csv(df, "rbench_differentmodels.csv")
 
 # scale dep 
 

### 2022-01-02 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@76c7b9ade5287eadc68d40ada1fbf3e0bf59a123 🚀
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@2097f05e0a19cd9b458269edabf1cd524a42f668 🚀

@@
 
+\begin{longtable}[]{@{}llllll@{}}
+\toprule
+Model & nlmpy? & NLMR & Description & Reference & Aliases\tabularnewline
+\midrule
+\endhead
+No gradient & x & x & & &\tabularnewline
+Planar gradient & x & x & & &\tabularnewline
+Distance gradient & x & x & & &\tabularnewline
+Random rectuangular cluster & x & x & & &\tabularnewline
+Random element nearest-neighbor & x & x* & & & \texttt{nlm\_mosaictess},
+k-means\tabularnewline
+Random cluster nearest-neighbor & x & x & & &\tabularnewline
+Random curds & & x & & &\tabularnewline
+Gaussian Field & & x & & &\tabularnewline
+Perlin noise & x & & & &\tabularnewline
+Diamond-square & & & & &\tabularnewline
+Mosaic random field & & x & & &\tabularnewline
+\bottomrule
+\end{longtable}
+
 In
@@
 In this section we show our implementation of MPD is faster than NLMR's
-C++ MPD across all scales, up to the asyptotic limit imposed by the
-\(O(n^2)\) scaling of the raster
+C++ MPD scales until the asyptotic limit imposed by the \(O(n^2)\)
+scaling of the raster
 
@@
 \centering
-\includegraphics{./figures/draftfig3.png}
+\includegraphics{./figures/figure3.png}
 \caption{Comparison of speed of generating a midpoint displacement

### 2022-01-07 src/02_differentmodels_bench.jl
up

@@ -1,116 +1,79 @@
 using DataFrames, CSV, DataFramesMeta
 using Plots
+using LaTeXStrings
+using Plots.PlotMeasures
+
+jl = CSV.read("src/benchmarking/artifacts/julia.csv", DataFrame)
+r = CSV.read("src/benchmarking/artifacts/r.csv", DataFrame) 
+r = filter(x-> "NA" ∉ x, r)
+r.sidelength = parse.(Float32, r.sidelength)
+r.meantime = parse.(Float32, r.meantime)
+
+py = CSV.read("src/benchmarking/artifacts/py.csv", DataFrame) 
+
+jlsets = (label="", mc=:dodgerblue)
+rsets = (label="", mc=:mediumpurple)
+pysets = (label="", mc=:green)
 
 
-jl = CSV.read("src/benchmarking/juliabench_differentmodels.csv", DataFrame)
-r = CSV.read("src/benchmarking/rbench_differentmodels.csv", DataFrame)
-py = CSV.read("src/benchmarking/pybench_differentmodels.csv", DataFrame)
+function makeplt(jl, r, py, name, titlestr)
 
-r.time = r.time_nanoseconds ./ 10^9
-jl.time = jl.time_nanoseconds ./ 10^9
-py.time = py.mean_execution_time
+    jldf, rdf, pydf = map(df->filter(x->x.model==name,df), [jl,r,py])
 
+    juliacolor = :dodgerblue
+    pycolor = :forestgreen
+    rcolor = :mediumpurple
 
-jlsets = (label="", mc=:dodgerblue, ma=0.01)
-rsets = (label="", mc=:mediumpurple, ma=0.01)
-pysets = (label="", mc=:green, ma=0.01)
+    markersettings = (ms=5,msw=2,ma=0.9)
+    linesettings = (ls=1.5)
+    ugh = [L"2^3", L"2^4", L"2^5", L"2^6", L"2^7", L"2^8", L"2^9", L"2^{10}", L"2^{11}", L"2^{12}"]
+ylab = [L"10^{-5}",L"10^{-4}",L"10^{-3}",L"10^{-2}",L"10^{-1}",L"10^{0}", L"10^{1}", L"10^{2}",  ]
 
[…]

### 2022-01-07 src/03_interoperable.jl

@@ -1,0 +1,20 @@
+using NeutralLandscapes
+using SimpleSDMLayers
+ENV["RASTERDATASOURCES_PATH"] = "/home/michael/data/"
+
+
+quebec = SimpleSDMPredictor(WorldClim, BioClim; left=-90., right=-50., top=75., bottom=40.)
+qcmask = fill(true, size(quebec)) 
+qcmask[findall(isnothing, quebec.grid)] .= false
+
+pltsettings = (cbar=:none, frame=:box)
+
+plot(
+    heatmap(rand(MidpointDisplacement(0.8), size(layer), mask=qcmask); pltsettings),
+    heatmap(rand(PlanarGradient(), size(layer), mask=qcmask); pltsettings),
+    heatmap(rand(PerlinNoise((4,4)), size(layer), mask=qcmask); pltsettings),
+    heatmap(rand(NearestNeighborCluster(0.5), size(layer), mask=qcmask); pltsettings),
+    dpi=400
+)
+
+savefig("interoperable.png")

### 2022-01-07 src/03_scale_bench.jl

@@ -1,59 +1,0 @@
-using CSV, DataFrames
-using DataFramesMeta
-using Plots
-using LaTeXStrings
-using Unitful: mm
-
-jl = CSV.read("src/benchmarking/juliascaling_means.csv", DataFrame)
-r = CSV.read("src/benchmarking/r_scalebench.csv", DataFrame)
-py = CSV.read("src/benchmarking/py_scalebench.csv", DataFrame)
-
-rgrp = groupby(r, :sidelength)
-rmean = @combine(rgrp, :time = mean(:time_sec))
-
-pygrp = groupby(py, :size)
-pymean = @combine(pygrp, :time = mean(:time_seconds))
-
-
-jl
-ugh = [L"2^3", L"2^4", L"2^5", L"2^6", L"2^7", L"2^8", L"2^9", L"2^{10}", L"2^{11}", L"2^{12}"]
-
-ylab = [L"10^{-5}",L"10^{-4}",L"10^{-3}",L"10^{-2}",L"10^{-1}",L"10^{0}", L"10^{1}", L"10^{2}",  ]
-
-plot(jl.side, jl.time_seconds, lw=1.5,lc=:dodgerblue,    label="NeutralLandscapes.jl")
-scatter!(jl.side, jl.time_seconds,
-    label="",
-    fontfamily = "computer modern",
-    xlabel="Raster side length",
-    ylabel="Execution time (seconds)",
-    frame=:box,
-    grid=:scientific,
-    legend=:outerright,
-    tickfontsize=10,
-    mc=:white,
-    msw=2,
-    ms=4,
-    ma=0.9,
-    msc=:dodgerblue,
-    yscale=:log10, 
-    xlim=(3,12.1),
-    yticks=([10.0^i for i in -5:2], ylab),
-    xticks=(3:12,ugh),
-    ylim=(10^-5, 10^1),
-    dpi=500,
-    size=(700, 450))
-
-
-plot!(log2.(rmean.sidelength), label="NLMR (using C++)", lc=:mediumpurple, rmean.time,lw=1.5, la=0.95)
-scatter!(log2.(rmean.sidelength), rmean.time, 
-    label="", msw=2, ms=4, mc=:white, msc=:mediumpurple, ma=0.9)
-
-
-plot!(log2.(pymean.size), pymean.time, label="nlmpy", lc=:green, la=0.95)
-scatter!(log2.(pymean.size), pymean.time, ms=4,
[…]

### 2022-01-07 src/benchmarking/juliabench.jl

@@ -2,57 +2,42 @@ using NeutralLandscapes
 using BenchmarkTools
 using Plots
 using DataFrames, CSV
+using StatsBase
+using Statistics
+
 ns = 1000
-siz = 250, 250
+df = DataFrame(model=[],sidelength=[], meantime=[], stdtime=[])
 
 
-pg = @benchmark rand(PlanarGradient(), siz) samples=ns
-eg = @benchmark rand(EdgeGradient(), siz)  samples=ns
-random = @benchmark rand(NoGradient(), siz)  samples=ns
-mpd = @benchmark rand(MidpointDisplacement(0.75), siz)  samples=ns
-nne = @benchmark rand(NearestNeighborElement(10), siz)  samples=ns
-nnc = @benchmark rand(NearestNeighborCluster(0.4), siz)  samples=ns
-rect = @benchmark rand(RectangularCluster(10,150), siz) samples=ns
-perlin = @benchmark rand(PerlinNoise((4,4)), siz) samples=ns
+for s in 3:12
+    @show s
+    rect = falses(2^s,2^s)
+    rect[1:5,1:5] .= true    
+    pg = @benchmark rand(PlanarGradient(), siz) samples=ns setup=(siz=(2^$s, 2^$s))
+    dg = @benchmark rand(DistanceGradient(findall(vec(r)))) setup=(siz=(2^$s, 2^$s), r=$rect)
+    #eg = @benchmark rand(EdgeGradient(), siz)  samples=ns setup=(siz=(2^$s, 2^$s))
+    random = @benchmark rand(NoGradient(), siz)  samples=ns setup=(siz=(2^$s, 2^$s))
+    mpd = @benchmark rand(MidpointDisplacement(0.75), siz)  samples=ns setup=(siz=(2^$s, 2^$s))
+    nne = @benchmark rand(NearestNeighborElement(10), siz) samples=ns setup=(siz=(2^$s, 2^$s))
+    perlin = @benchmark rand(PerlinNoise((4,4)), siz) samples=ns setup=(siz=(2^$s, 2^$s))
 
-
-
-pg, eg, random, mpd, nne, rect
-
-pgdf = DataFrame(model=["planar gradient" for i in 1:length(pg.times)], time_nanoseconds=pg.times)
-egdf = DataFrame(model=["edge gradient" for i in 1:length(eg.times)], time_nanoseconds=eg.times)
-randomdf = DataFrame(model=["random" for i in 1:length(random.times)], time_nanoseconds=random.times)
[…]

### 2022-01-07 src/benchmarking/python_bench.py

@@ -1,33 +1,43 @@
 from nlmpy import nlmpy
 import time
-
-nlm = nlmpy.mpd(nRow=50, nCol=50, h=0.75)
-
+import numpy
 
 methods = dict(
-    random = lambda: nlmpy.random(250,250), 
-    pg = lambda: nlmpy.planarGradient(250,250), 
-    dg = lambda: nlmpy.distanceGradient(nlmpy.planarGradient(250,250)), 
-    eg = lambda: nlmpy.edgeGradient(250,250),
-    ws = lambda: nlmpy.waveSurface(250,250, 4), 
-    mpd = lambda: nlmpy.mpd(256,256,0.8), 
-    perlin = lambda: nlmpy.perlinNoise(250,250, (2,2)),
-    renn = lambda: nlmpy.randomElementNN(250,250,10), 
-    rcnn = lambda: nlmpy.randomClusterNN(250,250, 0.4),  
+    random = lambda s: nlmpy.random(s,s), 
+    pg = lambda s: nlmpy.planarGradient(s,s), 
+    dg = lambda s: nlmpy.distanceGradient(nlmpy.planarGradient(s,s)), 
+    eg = lambda s: nlmpy.edgeGradient(s,s),
+    #ws = lambda: nlmpy.waveSurface(250,250, 4), 
+    mpd = lambda s: nlmpy.mpd(s,s,0.8), 
+    perlin = lambda s: nlmpy.perlinNoise(s,s, (2,2)),
+    nne = lambda s: nlmpy.randomElementNN(s,s,10), 
+    #rcnn = lambda: nlmpy.randomClusterNN(250,250, 0.4),  
 )
 
 nbatches = 1000
 import csv
-with open('pybench.csv', 'w') as csvfile:
-    writer = csv.writer(csvfile)
-    writer.writerow(["method", "batch", "mean_execution_time"])
+sidelengths = range(3, 11)
 
-    for key in methods: 
-        for batch in range(0,nbatches):
-            t1 = time.time()
-            r = methods[key]()
-            t2 = time.time()
-            writer.writerow([key, batch, t2-t1])
+
+
+with open('artifacts/py.csv', 'w') as csvfile:
+    writer = csv.writer(csvfile)
+    writer.writerow(["model", "size", "meantime", "stdtime"])
+
+    for s in sidelengths:
+        print(2**s)
+        for key in methods: 
+            sum = 0.0
+            vals = numpy.zeros(nbatches)
+            for batch in range(0,nbatches):
+                t1 = time.time()
[…]

### 2022-01-07 src/benchmarking/rbench.R

@@ -4,49 +4,57 @@
 library("NLMR")
 library("microbenchmark")
 
-rand = microbenchmark(nlm_random(250,250,1), times=1000)
-dg = microbenchmark(nlm_distancegradient(250,250, origin=c(1,1,1,1)), times=1000)
-eg = microbenchmark(nlm_edgegradient(250,250), times=1000)
-mpd = microbenchmark(nlm_mpd(256, 256), times=1000)
-rrc = microbenchmark(nlm_randomrectangularcluster(250,250, minl=10, maxl=150), times=1000)
-nne = microbenchmark(nlm_mosaictess(250,250,germs=10),times=1000)
-#nnc = microbenchmark(nlm_randomcluster(250,250, p=0.4),times=1000)
 
-df = data.frame(matrix(nrow=1,ncol=3))
-colnames(df) = c("model", "replicate", "time_nanoseconds")
+makedf = function(df, modeldf, name, s){
+    newdf = data.frame(matrix(nrow=1,ncol=4))
+    colnames(newdf) = c("model", "sidelength", "meantime", "stdtime")
 
-makedf = function(df, modeldf, name){
-    newdf = data.frame(matrix(nrow=1000,ncol=3))
-    colnames(newdf) = c("model", "replicate", "time_nanoseconds")
+    newdf$model = c(name)
+    newdf$sidelength = c(s)
+    newdf$meantime = mean(modeldf$time) / 10^9   # convert from ns
+    newdf$stdtime = sd(modeldf$time) / 10^9      # convert from ns 
 
-    newdf$model = rep(name, 1000)
-    newdf$replicate = seq(1,1000)
-    newdf$time_nanoseconds = modeldf$time
     return(rbind(df, newdf))
 }
 
-df = makedf(df, rand, "random")
-df = makedf(df, dg, "distance gradient")
-df = makedf(df, eg, "edge gradient")
-df = makedf(df, mpd, "midpoint displacement")
-df = makedf(df, rrc, "rectangle cluster")
-df = makedf(df, nne, "nearest neighbor element")
 
-write.csv(df, "rbench_differentmodels.csv")
+makebenchforallmodels = function (sz){
 
-# scale dep 
+    rectsmall = max(as.integer(0.05*sz[1]), 1)
+    rectlarge =  as.integer(0.4*sz[1])
 
[…]

### 2022-01-07 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@0303cabf9d137dc149a9b232d9cffde6e3e86443 🚀

--- 2022-01-01 draft.tex
@@
 
-In
+\begin{longtable}[]{@{}llllll@{}}
+\toprule
+\begin{minipage}[b]{0.35\columnwidth}\raggedright
+Model\strut
+\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedright
+nlmpy?\strut
+\end{minipage} & \begin{minipage}[b]{0.05\columnwidth}\raggedright
+NLMR\strut
+\end{minipage} & \begin{minipage}[b]{0.33\columnwidth}\raggedright
+Description\strut
+\end{minipage} & \begin{minipage}[b]{0.02\columnwidth}\raggedright
+Reference\strut
+\end{minipage} & \begin{minipage}[b]{0.02\columnwidth}\raggedright
+Aliases\strut
+\end{minipage}\tabularnewline
+\midrule
+\endhead
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+No gradient\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+Each cell is drawn randomly\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Planar gradient\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+A gradient from low to high at a given angle\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Distance gradient\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+Each cell is the distance between that cell and a location\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Random rectuangular cluster\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+Covers the plane in random rectanges until covered\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Random element nearest-neighbor\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x*\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+Discrete categories based on distance a set of \texttt{n} random
+points\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\texttt{nlm\_mosaictess}, k-means\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Random cluster nearest-neighbor\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+Starts with \(n\) seed points and grows clusters probabilistically\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Random curds\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Gaussian Field\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Diamond-square\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+Improvement on Diamond-square and fractal brownian motion.\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Perlin noise\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+Method for noise with ``smoother'' features than DS/MPD\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.35\columnwidth}\raggedright
+Mosaic random field\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
+x\strut
+\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 
+\begin{verbatim}
+using NeutralLandscapes
+using SimpleSDMLayers
+
+quebec = SimpleSDMPredictor(WorldClim, BioClim; left=-90., right=-50., top=75., bottom=40.)
+qcmask = fill(true, size(quebec)) 
+qcmask[findall(isnothing, quebec.grid)] .= false
+
+pltsettings = (cbar=:none, frame=:box)
+
+plot(
+    heatmap(rand(MidpointDisplacement(0.8), size(layer), mask=qcmask); pltsettings),
+    heatmap(rand(PlanarGradient(), size(layer), mask=qcmask); pltsettings),
+    heatmap(rand(PerlinNoise((4,4)), size(layer), mask=qcmask); pltsettings),
+    heatmap(rand(NearestNeighborCluster(0.5), size(layer), mask=qcmask); pltsettings),
+    dpi=400
+)
+
+savefig("interoperable.png")
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{./figures/interoperable.png}
+\caption{todo}
+\end{figure}
+
 \hypertarget{benchmark-comparison-to-nlmpy-and-nlmr}{%
@@
 
-\textbf{Fig 2}: Benchmark comparison of selected methods in each of the
-three languages
-
-In fig 2 we should a selection of neutral landscape generators (random,
-edge gradient, perlin noise, distance-gradient)
-
-\hypertarget{mpd-comparison}{%
-\subsection{MPD comparison}\label{mpd-comparison}}
-
-Why use this particular generator as the comparison? It's slow. So slow
-that NLMR implements it in C++. (NLMR implements both MPD, neighbor,
-randrect, and random neighboorhood in c++). Still these three
-algorithms, which cosinsts of 3/16 of NLMR's alg implementations,
-constitute 33\% of its codebase.
-
-In this section we show our implementation of MPD is faster than NLMR's
-C++ MPD across all scales, up to the asyptotic limit imposed by the
-\(O(n^2)\) scaling of the raster
-
 \begin{figure}
 \centering
-\includegraphics{./figures/draftfig3.png}
-\caption{Comparison of speed of generating a midpoint displacement
-neutral landscape (y-axis) against raster size (measured as length of
-the size of a square raster, x-axis)}
+\includegraphics{./figures/benchmark.png}
+\caption{todo}
 \end{figure}
@@
 
-\(M_t = f(M_{t-1})\)
+\(M_t = M_{t-1} + f(M(t-1))\)
+
+\hypertarget{models-of-change}{%
+\subsection{Models of change}\label{models-of-change}}
+
+\hypertarget{directional}{%
+\subsubsection{Directional}\label{directional}}
+
+\hypertarget{temporally-autocorrelation}{%
+\subsubsection{Temporally
+autocorrelation}\label{temporally-autocorrelation}}
+
+\(r\): rate, \(v\): variability, \(U\) matrix of draws from standard
+\(\text{Normal}(0,1)\)
+
+\(f_{T}(M_{ij}) = r + vU_{ij}\)
+
+\hypertarget{spatial-autocorrelation}{%
+\subsubsection{Spatial autocorrelation}\label{spatial-autocorrelation}}
+
+\(r\): rate, \(v\): variability, \([Z(\delta)]_{ij}\): the \((i,j)\)
+entry of the zscore of the \(\delta\) matrix
+
+\(f_{S}(M_{ij}) = r + v \cdot [Z(\delta)]_{ij}\)
+
+\hypertarget{spatiotemporal-autocorrelation}{%
+\subsubsection{Spatiotemporal
+autocorrelation}\label{spatiotemporal-autocorrelation}}
+
+\hypertarget{rescaling-to-mimic-real-data}{%
+\subsection{Rescaling to mimic real
+data}\label{rescaling-to-mimic-real-data}}
 

### 2022-01-07 src/02_differentmodels_bench.jl
up

@@ -27,7 +27,7 @@ function makeplt(jl, r, py, name, titlestr)
     markersettings = (ms=5,msw=2,ma=0.9)
     linesettings = (ls=1.5)
     ugh = [L"2^3", L"2^4", L"2^5", L"2^6", L"2^7", L"2^8", L"2^9", L"2^{10}", L"2^{11}", L"2^{12}"]
-ylab = [L"10^{-5}",L"10^{-4}",L"10^{-3}",L"10^{-2}",L"10^{-1}",L"10^{0}", L"10^{1}", L"10^{2}",  ]
+ylab = [L"10^{-6}",L"10^{-5}",L"10^{-4}",L"10^{-3}",L"10^{-2}",L"10^{-1}",L"10^{0}", L"10^{1}", L"10^{2}",  ]
 
     plot(log2.(jldf.sidelength), jldf.meantime; linesettings)
     title!(titlestr)
@@ -42,9 +42,9 @@ ylab = [L"10^{-5}",L"10^{-4}",L"10^{-3}",L"10^{-2}",L"10^{-1}",L"10^{0}", L"10^{
         mc=juliacolor,
         msc=juliacolor,
         yscale=:log10, 
-        ylim=(10^-5, 10^2),
+        ylim=(10^-6, 10^1),
         xlim=(3,12.1),
-        yticks=([10.0^i for i in -5:2], ylab),
+        yticks=([10.0^i for i in -6:1], ylab),
         xticks=(3:12,ugh),
         dpi=500,
         size=(300, 300); markersettings...)

### 2022-01-07 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@ad021b39d7baa9690157c03e794ab7575ed9aba8 🚀

@@
 Neutral landscapes are increasingly used in ecological and evolutionary
-studies to provide a null expectation of the variance of a given metric
-over space.
+studies to provide a null expectation spatial variation of a given
+measurement. Originally developed to simulate the spatially
+autocorrelated data (\textbf{Gardner1987NeuMod?};
+\textbf{Milne1992SpaAgg?}), the have seen use in a wide range of
+disciplines: from landscape genetics (\textbf{Storfer2007PutLan?}), to
+landscape and spatial ecology (\textbf{Tinker2004HisRan?};
+\textbf{Remmel2013CatCla?}), and biogeography
+(\textbf{Albert2017BarDis?}).
 
-Wide range of disciplines: from landscape genetics {[}{]}, to spatial
-ecology {[}{]}, and biogeography {[}{]}.
-
+The two primary packages used to simulate neutral landscapes are
+\texttt{NLMR} in (the \texttt{R} language) (\textbf{Sciaini2018NlmLan?})
+and \texttt{NLMpy} (in Python; \textbf{Etherington2015NlmPyt?}). We
+present \texttt{NeutralLandscapes.jl}, a package in \texttt{Julia} for
+neutral landscapes which is faster than both above package. Here we
+demonstrate that \texttt{NeutralLandscapes.jl}, depending on the method,
+is orders of magnitude faster than previous neutral landscape packages.
 As biodiversity science becomes increasingly concerned with temporal
-change and its consequences, its clear there is a gap generating neutral
-landscapes that change over time. In this ms we present how
-\texttt{NeutralLandscapes.jl} is orders of magnitudes faster than
-packages \texttt{nlmpy} (in python) or \texttt{NLMR} (in R). In addition
-we then present a novel method for generating landscape change with
-prescribed levels of spatial and temporal autocorrelation.
+change and its consequences, its clear there is a gap in methodology in
+generating neutral landscapes that change over time. In addition we
+present a novel method for generating landscape change with prescribed
+levels of spatial and temporal autocorrelation, which is implemented in
+\texttt{NeutralLandscapes.jl}
 
@@
 fig.~\ref{fig:allmethods} shows a replica of Figure 1 from
-(\textbf{nlmpycite?}), which shows the capacity of the library to
-generate different types of neutral landscapes, and then apply masks and
-categorical classifcation to them.
-
-Table of methods.
-
-\begin{longtable}[]{@{}llllll@{}}
-\toprule
-\begin{minipage}[b]{0.35\columnwidth}\raggedright
-Model\strut
-\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedright
-nlmpy?\strut
-\end{minipage} & \begin{minipage}[b]{0.05\columnwidth}\raggedright
-NLMR\strut
-\end{minipage} & \begin{minipage}[b]{0.33\columnwidth}\raggedright
-Description\strut
-\end{minipage} & \begin{minipage}[b]{0.02\columnwidth}\raggedright
-Reference\strut
-\end{minipage} & \begin{minipage}[b]{0.02\columnwidth}\raggedright
-Aliases\strut
-\end{minipage}\tabularnewline
-\midrule
-\endhead
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-No gradient\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-Each cell is drawn randomly\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Planar gradient\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-A gradient from low to high at a given angle\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Distance gradient\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-Each cell is the distance between that cell and a location\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Random rectuangular cluster\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-Covers the plane in random rectanges until covered\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Random element nearest-neighbor\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x*\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-Discrete categories based on distance a set of \texttt{n} random
-points\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\texttt{nlm\_mosaictess}, k-means\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Random cluster nearest-neighbor\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-Starts with \(n\) seed points and grows clusters probabilistically\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Random curds\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Gaussian Field\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Diamond-square\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-Improvement on Diamond-square and fractal brownian motion.\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Perlin noise\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-Method for noise with ``smoother'' features than DS/MPD\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.35\columnwidth}\raggedright
-Mosaic random field\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedright
-x\strut
-\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage} & \begin{minipage}[t]{0.02\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\bottomrule
-\end{longtable}
+(\textbf{Etherington2015NlmPyt?}), which shows the capacity of the
+library to generate different types of neutral landscapes, and then
+apply masks and categorical classifcation to them.
 
@@
 \end{figure}
-
-\hypertarget{what-methods-have-been-called-different-things-but-are-actually-the-same-thing}{%
-\subsection{What methods have been called different things but are
-actually the same
-thing?}\label{what-methods-have-been-called-different-things-but-are-actually-the-same-thing}}
 
@@
 
+\(f_{ST}(M_{ij}) = r + v \cdot [Z(\delta)]_{ij}\)
+
 \hypertarget{rescaling-to-mimic-real-data}{%

### 2022-01-07 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@b480dd4c81c2bfa8ff58caa5e9a1202fef359f8b 🚀

@@
 measurement. Originally developed to simulate the spatially
-autocorrelated data (\textbf{Gardner1987NeuMod?};
-\textbf{Milne1992SpaAgg?}), the have seen use in a wide range of
-disciplines: from landscape genetics (\textbf{Storfer2007PutLan?}), to
-landscape and spatial ecology (\textbf{Tinker2004HisRan?};
-\textbf{Remmel2013CatCla?}), and biogeography
-(\textbf{Albert2017BarDis?}).
+autocorrelated data (Gardner \emph{et al.} 1987; Milne 1992), the have
+seen use in a wide range of disciplines: from landscape genetics
+(Storfer \emph{et al.} 2007), to landscape and spatial ecology (Tinker
+\emph{et al.} 2004; Remmel \& Fortin 2013), and biogeography (Albert
+\emph{et al.} 2017).
 
 The two primary packages used to simulate neutral landscapes are
-\texttt{NLMR} in (the \texttt{R} language) (\textbf{Sciaini2018NlmLan?})
-and \texttt{NLMpy} (in Python; \textbf{Etherington2015NlmPyt?}). We
+\texttt{NLMR} in (the \texttt{R} language) (Sciaini \emph{et al.} 2018)
+and \texttt{NLMpy} (in Python; Etherington \emph{et al.} 2015). We
 present \texttt{NeutralLandscapes.jl}, a package in \texttt{Julia} for
@@
 
-fig.~\ref{fig:allmethods} shows a replica of Figure 1 from
-(\textbf{Etherington2015NlmPyt?}), which shows the capacity of the
-library to generate different types of neutral landscapes, and then
-apply masks and categorical classifcation to them.
+fig.~\ref{fig:allmethods} shows a replica of Figure 1 from Etherington
+\emph{et al.} (2015), which shows the capacity of the library to
+generate different types of neutral landscapes, and then apply masks and
+categorical classifcation to them.
 
@@
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Albert2017BarDis}{}%
+Albert, J.S., Schoolmaster, D.R., JR., Tagliacollo, V. \&
+Duke-Sylvester, S.M. (2017). Barrier Displacement on a Neutral
+Landscape: Toward a Theory of Continental Biogeography. \emph{Systematic
+Biology}, 66, 167--182.
+
+\leavevmode\hypertarget{ref-Etherington2015NlmPyt}{}%
+Etherington, T.R., Holland, E.P. \& O'Sullivan, D. (2015). NLMpy: A
+python software package for the creation of neutral landscape models
+within a general numerical framework. \emph{Methods in Ecology and
+Evolution}, 6, 164--168.
+
+\leavevmode\hypertarget{ref-Gardner1987NeuMod}{}%
+Gardner, R.H., Milne, B.T., Turnei, M.G. \& O'Neill, R.V. (1987).
+Neutral models for the analysis of broad-scale landscape pattern.
+\emph{Landscape Ecology}, 1, 19--28.
+
+\leavevmode\hypertarget{ref-Milne1992SpaAgg}{}%
+Milne, B.T. (1992). Spatial Aggregation and Neutral Models in Fractal
+Landscapes. \emph{The American Naturalist}, 139, 32--57.
+
+\leavevmode\hypertarget{ref-Remmel2013CatCla}{}%
+Remmel, T.K. \& Fortin, M.-J. (2013). Categorical, class-focused map
+patterns: Characterization and comparison. \emph{Landscape Ecology}, 28,
+1587--1599.
+
+\leavevmode\hypertarget{ref-Sciaini2018NlmLan}{}%
+Sciaini, M., Fritsch, M., Scherer, C. \& Simpkins, C.E. (2018). NLMR and
+landscapetools: An integrated environment for simulating and modifying
+neutral landscape models in R. \emph{Methods in Ecology and Evolution},
+9, 2240--2248.
+
+\leavevmode\hypertarget{ref-Storfer2007PutLan}{}%
+Storfer, A., Murphy, M.A., Evans, J.S., Goldberg, C.S., Robinson, S.,
+Spear, S.F., \emph{et al.} (2007). Putting the {``landscape''} in
+landscape genetics. \emph{Heredity}, 98, 128--142.
+
+\leavevmode\hypertarget{ref-Tinker2004HisRan}{}%
+Tinker, D., Romme, W.H. \& Despain, D. (2004). Historic range of
+variability in landscape structure in subalpine forests of the Greater
+Yellowstone Area, USA. \emph{Landscape Ecology}.
+
+\end{CSLReferences}
 

### 2022-01-07 src/benchmarking/juliabench.jl
up

@@ -5,7 +5,7 @@ using DataFrames, CSV
 using StatsBase
 using Statistics
 
-ns = 1000
+ns = 250
 df = DataFrame(model=[],sidelength=[], meantime=[], stdtime=[])
 
 
@@ -13,13 +13,13 @@ for s in 3:12
     @show s
     rect = falses(2^s,2^s)
     rect[1:5,1:5] .= true    
-    pg = @benchmark rand(PlanarGradient(), siz) samples=ns setup=(siz=(2^$s, 2^$s))
-    dg = @benchmark rand(DistanceGradient(findall(vec(r)))) setup=(siz=(2^$s, 2^$s), r=$rect)
-    #eg = @benchmark rand(EdgeGradient(), siz)  samples=ns setup=(siz=(2^$s, 2^$s))
-    random = @benchmark rand(NoGradient(), siz)  samples=ns setup=(siz=(2^$s, 2^$s))
-    mpd = @benchmark rand(MidpointDisplacement(0.75), siz)  samples=ns setup=(siz=(2^$s, 2^$s))
-    nne = @benchmark rand(NearestNeighborElement(10), siz) samples=ns setup=(siz=(2^$s, 2^$s))
-    perlin = @benchmark rand(PerlinNoise((4,4)), siz) samples=ns setup=(siz=(2^$s, 2^$s))
+    pg = @benchmark rand(PlanarGradient(), 2^$s, 2^$s) samples=ns 
+    dg = @benchmark rand(DistanceGradient(findall(vec(r))), 2^$s, 2^$s) samples=ns setup=(r=$rect)
+    eg = @benchmark rand(EdgeGradient(), 2^$s, 2^$s)  samples=ns 
+    random = @benchmark rand(NoGradient(), 2^$s, 2^$s)  samples=ns 
+    mpd = @benchmark rand(MidpointDisplacement(0.75), 2^$s, 2^$s)  samples=ns 
+    nne = @benchmark rand(NearestNeighborElement(10), 2^$s, 2^$s) samples=ns 
+    perlin = @benchmark rand(PerlinNoise((4,4)), 2^$s, 2^$s) samples=ns 
 
     models = Dict("pg" => pg, 
     "eg" => eg, 

### 2022-01-07 src/benchmarking/python_bench.py

@@ -14,9 +14,9 @@ methods = dict(
     #rcnn = lambda: nlmpy.randomClusterNN(250,250, 0.4),  
 )
 
-nbatches = 1000
+nbatches = 250
 import csv
-sidelengths = range(3, 11)
+sidelengths = range(3, 13)
 
 
 
@@ -27,17 +27,21 @@ with open('artifacts/py.csv', 'w') as csvfile:
     for s in sidelengths:
         print(2**s)
         for key in methods: 
-            sum = 0.0
-            vals = numpy.zeros(nbatches)
-            for batch in range(0,nbatches):
-                t1 = time.time()
-                r = methods[key](2**s)
-                t2 = time.time()
 
-                vals[batch] = t2-t1
-            mn = numpy.mean(vals)
-            sdev = numpy.std(vals)
-            writer.writerow([key, s, mn, sdev])
+            if key == "mpd" and s > 10:
+                break
+            else:
+                sum = 0.0
+                vals = numpy.zeros(nbatches)
+                for batch in range(0,nbatches):
+                    t1 = time.time()
+                    r = methods[key](2**s)
+                    t2 = time.time()
+
+                    vals[batch] = t2-t1
+                mn = numpy.mean(vals)
+                sdev = numpy.std(vals)
+                writer.writerow([key, s, mn, sdev])
 
             
 """

### 2022-01-07 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@bda89e4da88d5b6854a5b28b5327f7914790a718 🚀
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@e2a240feba5ca8d423db8b5bb2a9afc549c7f19a 🚀

@@
 
-The two primary packages used to simulate neutral landscapes are
-\texttt{NLMR} in (the \texttt{R} language) (Sciaini \emph{et al.} 2018)
-and \texttt{NLMpy} (in Python; Etherington \emph{et al.} 2015). We
-present \texttt{NeutralLandscapes.jl}, a package in \texttt{Julia} for
-neutral landscapes which is faster than both above package. Here we
-demonstrate that \texttt{NeutralLandscapes.jl}, depending on the method,
-is orders of magnitude faster than previous neutral landscape packages.
+We present \texttt{NeutralLandscapes.jl}, a package in \texttt{Julia}
+for neutral landscapes. The two primary packages used to simulate
+neutral landscapes are \texttt{NLMR} in (the \texttt{R} language)
+(Sciaini \emph{et al.} 2018) and \texttt{NLMpy} (in Python; Etherington
+\emph{et al.} 2015). Here we demonstrate that
+\texttt{NeutralLandscapes.jl}, depending on the method, is orders of
+magnitude faster than previous neutral landscape packages.
+
 As biodiversity science becomes increasingly concerned with temporal
@@
 )
-
-savefig("interoperable.png")
 \end{verbatim}

### 2022-01-07 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@2b50de832021e47bf438674ffd58123c91cffb27 🚀

@@
 It's fast. As the scale and resolution of raster data increases, neutral
-models must be able to scale to match those data dimensions. Here we
-provide two benchmark tests. First a comparison of the speed variety of
-methods from each \texttt{NeutralLandscapes.jl}, \texttt{NLMR}, and
-\texttt{nlmpy}. Second we compare these performance of each of these
-software packages as rasters become larger. We show that \texttt{Julia}
-even outperforms the \texttt{NLMR} via C++ implemention of a
-particularly slow neutral landscape method (midpoint displacement).
+models must be able to scale to match those data dimensions.
 

### 2022-01-08 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@5fae74e2a5f1bfa0bf3c1d9a8d8a862b337a5613 🚀

@@
 We implement methods for generating change that are temporally
-autocorrelated, spatially autocorrelated, or both.
+autocorrelated, spatially-autocorrelated, or both.
 
@@
 \(r\): rate, \(v\): variability, \(U\) matrix of draws from standard
-\(\text{Normal}(0,1)\)
+\(\text{Normal}(0,1)\).
+
+Here \(v\) replects the amount of temporal autocorrelation.
 
@@
 
+Results in an expected value of change of \(r\) per timestep with
+variance \(v\).
+
 \hypertarget{spatial-autocorrelation}{%
 \subsubsection{Spatial autocorrelation}\label{spatial-autocorrelation}}
+
+Generate a matrix \(\delta\) with a NL generator.
 
@@
 \(f_{ST}(M_{ij}) = r + v \cdot [Z(\delta)]_{ij}\)
+
+\begin{figure}
+\centering
+\includegraphics{./figures/temporal.png}
+\caption{todo}
+\end{figure}
 

### 2022-03-16 src/02_differentmodels_bench.jl
rejection sampling abc

@@ -3,26 +3,29 @@ using Plots
 using LaTeXStrings
 using Plots.PlotMeasures
 
-jl = CSV.read("src/benchmarking/artifacts/julia.csv", DataFrame)
+jl = CSV.read("src/benchmarking/artifacts/julia_faster.csv", DataFrame)
 r = CSV.read("src/benchmarking/artifacts/r.csv", DataFrame) 
 r = filter(x-> "NA" ∉ x, r)
 r.sidelength = parse.(Float32, r.sidelength)
 r.meantime = parse.(Float32, r.meantime)
 
-py = CSV.read("src/benchmarking/artifacts/py.csv", DataFrame) 
+py = CSV.read("src/benchmarking/artifacts/py_singlethread.csv", DataFrame) 
 
 jlsets = (label="", mc=:dodgerblue)
 rsets = (label="", mc=:mediumpurple)
 pysets = (label="", mc=:green)
 
 
-function makeplt(jl, r, py, name, titlestr)
+function makeplt(jl, r, py, name, titlestr; leg=false)
 
     jldf, rdf, pydf = map(df->filter(x->x.model==name,df), [jl,r,py])
 
     juliacolor = :dodgerblue
     pycolor = :forestgreen
     rcolor = :mediumpurple
+
+    jllab, rlab, pylab = leg ? ["NeutralLandscapes.jl", "NLMR", "NLMpy"] : ["", "", ""]
+    legpos = leg ? Symbol("bottomright") : Symbol("none")
 
     markersettings = (ms=5,msw=2,ma=0.9)
     linesettings = (ls=1.5)
@@ -32,7 +35,7 @@ ylab = [L"10^{-6}",L"10^{-5}",L"10^{-4}",L"10^{-3}",L"10^{-2}",L"10^{-1}",L"10^{
     plot(log2.(jldf.sidelength), jldf.meantime; linesettings)
     title!(titlestr)
     scatter!(log2.(jldf.sidelength), jldf.meantime,
-        label="",
+        label=jllab,
         fontfamily = "computer modern",
         xlabel="Raster side length",
         ylabel="Execution time (seconds)",
@@ -46,34 +49,34 @@ ylab = [L"10^{-6}",L"10^{-5}",L"10^{-4}",L"10^{-3}",L"10^{-2}",L"10^{-1}",L"10^{
         xlim=(3,12.1),
         yticks=([10.0^i for i in -6:1], ylab),
[…]

### 2022-03-16 src/03_interoperable.jl

@@ -1,20 +1,38 @@
 using NeutralLandscapes
 using SimpleSDMLayers
+using Plots
 ENV["RASTERDATASOURCES_PATH"] = "/home/michael/data/"
 
 
-quebec = SimpleSDMPredictor(WorldClim, BioClim; left=-90., right=-50., top=75., bottom=40.)
+quebec = SimpleSDMPredictor(WorldClim, BioClim; left=-150., right=-50., top=75., bottom=45.)
 qcmask = fill(true, size(quebec)) 
 qcmask[findall(isnothing, quebec.grid)] .= false
 
 pltsettings = (cbar=:none, frame=:box)
 
 plot(
-    heatmap(rand(MidpointDisplacement(0.8), size(layer), mask=qcmask); pltsettings),
-    heatmap(rand(PlanarGradient(), size(layer), mask=qcmask); pltsettings),
-    heatmap(rand(PerlinNoise((4,4)), size(layer), mask=qcmask); pltsettings),
-    heatmap(rand(NearestNeighborCluster(0.5), size(layer), mask=qcmask); pltsettings),
+    heatmap(rand(MidpointDisplacement(0.8), size(quebec), mask=qcmask); pltsettings),
+    heatmap(rand(PlanarGradient(), size(quebec), mask=qcmask); pltsettings),
+    heatmap(rand(PerlinNoise((4,4)), size(quebec), mask=qcmask); pltsettings),
+    heatmap(rand(NearestNeighborCluster(0.5), size(quebec), mask=qcmask); pltsettings),
     dpi=400
 )
 
 savefig("interoperable.png")
+
+
+
+heatmap(rand(MidpointDisplacement(0.8), size(quebec), mask=qcmask); frame=:none, c=:cork, axis=:none, colorbar=:none, pltsettings)
+savefig("etc.png")
+
+heatmap(rand(PerlinNoise((6,6)), size(quebec), mask=qcmask); frame=:none, axis=:none, colorbar=:none, pltsettings)
+savefig("access.png")
+
+heatmap(rand(MidpointDisplacement(0.2), size(quebec), mask=qcmask); frame=:none, axis=:none, colorbar=:none, c=:viridis)
+savefig("climvelocity.png")
+
+heatmap(rand(MidpointDisplacement(0.3), size(quebec), mask=qcmask); frame=:none, axis=:none, colorbar=:none, pltsettings)
+
+
[…]

### 2022-03-16 src/04_inference.jl

@@ -1,0 +1,85 @@
+using NeutralLandscapes
+using SimpleSDMLayers
+using SimpleSDMLayers: boundingbox
+using Plots
+using Distributions
+using LinearAlgebra
+using GeoStats
+using StatsBase
+using Random
+using GeoStatsBase
+using StatsPlots
+
+ENV["SDMLAYERS_PATH"] = "/home/michael/data/"
+ENV["RASTERDATASOURCES_PATH"] = "/home/michael/data/"
+
+# ENV["SDMLAYERS_PATH"] = "/project/def-gonzalez/mcatchen/data/"
+# ENV["RASTERDATASOURCES_PATH"] = "/project/def-gonzalez/mcatchen/data"
+
+rawtemp = convert(Float16, SimpleSDMPredictor(CHELSA, BioClim, 1; left=-77, right=-70.0, bottom=44.0, top=49.0))
+
+temp = coarsen(SimpleSDMPredictor(rawtemp.grid[1:600,1:800], boundingbox(rawtemp)...), StatsBase.mean, (8,8))
+plot(temp)
+temp = broadcast(x->1.0 - (maximum(temp) - x)/(maximum(temp) - minimum(temp)), temp)
+xspace,yspace = (temp.right - temp.left) / size(temp)[1], (temp.top -temp.bottom) / size(temp)[2]
+covergrid = map(x->isnothing(x) ? 0. : x, temp.grid)
+geogrid = georef((cover=convert(Matrix{Float16}, covergrid),), origin=(temp.left,temp.right), spacing=(xspace,yspace))
+
+#coraselc = coarsen(temp, x->nn_combine(countmap(x)), (8,8))
+#xspace,yspace = (coarselandcover.right - coarselandcover.left) / size(coarselandcover)[1], (coarselandcover.top - coarselandcover.bottom) / size(coarselandcover)[2]
+#geogrid = georef((cover=convert(Matrix{Float16}, coarselandcover.grid),), origin=(coarselandcover.left,coarselandcover.right), spacing=(xspace,yspace))
+
+function propose(θ)    
+   # vals = [v for v in shuffle!(collect(values(countmap(coarselandcover.grid))))]
+   # pdfs = vals ./sum(vals)
+   # cutoffs = vcat([0],[sum(pdfs[1:x]) for x in 1:length(pdfs)],[1])
+
+
+    mpd = rand(MidpointDisplacement(θ), size(temp))
+  #=  for i in eachindex(mpd)
+        for j in 1:length(cutoffs)-1
[…]

### 2022-03-16 src/benchmarking/python_bench.py

@@ -1,4 +1,8 @@
 from nlmpy import nlmpy
+import os
+
+os.environ['MKL_NUM_THREADS'] = '1'
+os.environ['OPENBLAS_NUM_THREADS'] = '1'
 import time
 import numpy
 
@@ -20,7 +24,7 @@ sidelengths = range(3, 13)
 
 
 
-with open('artifacts/py.csv', 'w') as csvfile:
+with open('artifacts/py_singlethread.csv', 'w') as csvfile:
     writer = csv.writer(csvfile)
     writer.writerow(["model", "size", "meantime", "stdtime"])
 

### 2022-03-16 src/04_inference.jl
smc update

@@ -46,40 +46,46 @@ function propose(θ)
     return SimpleSDMPredictor(mpd, boundingbox(temp)...) 
 end
 
-function ABC(prior)
+# difference is proposal score - current score
+acceptprobability(difference, α) = 1.0/(1.0+exp(-α*difference))
+
+function ABC(prior, α=1000)
     true_variogram = EmpiricalVariogram(geogrid, :cover)
    
-    numsteps = 100
-    ϵ = 0.00001
+    numsteps = 1000
 
-    hs = zeros(numsteps)
-    errors = zeros(numsteps)
+    Hchain = zeros(numsteps)
+    currentscore = zeros(numsteps)
 
-    cursor = 1
-    count = 1
-    while cursor < numsteps
+    currentscore[begin] = 1.0
+    for s in 2:numsteps
         H = rand(prior)
         proposal = propose(H)
         testgrid = georef((cover=convert(Matrix{Float16}, proposal.grid),), origin=(rawtemp.left,rawtemp.right), spacing=(xspace,yspace))
         test_variogram = EmpiricalVariogram(testgrid, :cover)
-        rmse = sum((true_variogram.ordinate .- test_variogram.ordinate).^2)
-        count += 1
-        if rmse < ϵ
-            errors[cursor] = rmse
-            hs[cursor] = H
-            cursor += 1
-            if cursor % 5 == 0 
-                @info cursor
-                @show "acceptrate = $(cursor/count)" 
-            end
-        end 
         
+        proposal_rmse = sum((true_variogram.ordinate .- test_variogram.ordinate).^2)
+        current_rmse = currentscore[s-1]
+        
+        p = acceptprobability(current_rmse-proposal_rmse, α)
+        if rand() < p
+            currentscore[s] = proposal_rmse
+            Hchain[s] = H
+        else  
+            currentscore[s] = currentscore[s-1]
+            Hchain[s] = Hchain[s-1]
+        end 
+        if s % 100 == 0 
+            @info s
+        end     
     end
-    return hs, errors
+    return Hchain, currentscore
 end
 
 ### TODO rescale temp to 0,1 
-@time hs, error = ABC(Uniform(0,1))
+@time hs, error = ABC(Uniform(0,1), 10^5.5)
 
 
-histogram(hs, bins=0:0.05:1)
+burnin = 100
+
[…]

### 2022-03-17 src/04_inference.jl
update with abc example

@@ -19,7 +19,7 @@ ENV["RASTERDATASOURCES_PATH"] = "/home/michael/data/"
 rawtemp = convert(Float16, SimpleSDMPredictor(CHELSA, BioClim, 1; left=-77, right=-70.0, bottom=44.0, top=49.0))
 
 temp = coarsen(SimpleSDMPredictor(rawtemp.grid[1:600,1:800], boundingbox(rawtemp)...), StatsBase.mean, (8,8))
-plot(temp)
+tempplt = plot(temp, cbar=:none, frame=:box, xlabel="Longitude", ylabel="Longitude")
 temp = broadcast(x->1.0 - (maximum(temp) - x)/(maximum(temp) - minimum(temp)), temp)
 xspace,yspace = (temp.right - temp.left) / size(temp)[1], (temp.top -temp.bottom) / size(temp)[2]
 covergrid = map(x->isnothing(x) ? 0. : x, temp.grid)
@@ -87,5 +87,22 @@ end
 
 
 burnin = 100
+histogram(hs[burnin:end], bins=0:0.025:1, frame=:box, label="", xlim=(0,1), xlabel="H", ylabel="Posterior Frequency", size=(500,500), dpi=250, c=:mediumpurple4, fa=0.5)
 
-histogram(hs[100:end], bins=0:0.025:1, frame=:box, label="", xlim=(0,1), xlabel="H", ylabel="Posterior Frequency", size=(500,500), dpi=250, c=:mediumpurple4, fa=0.5)
+
+
+
+using Plots, CSV, DataFrames
+
+df = CSV.read("./src/posterior_H.csv", DataFrame)
+
+histplt =histogram(df.posterior_H, legend=:topleft, label="Posterior", bins=0:0.01:1, normalize=:probability, fc=:steelblue4, fa=0.5, frame=:box, size=(500,500), dpi=300, xlim=(0,1))
+hline!([0.01], label="Prior", lw=2, c=:forestgreen)
+
+xlabel!("H")
+ylabel!("Probability")
+
+
+using UnitfulPlots
+plot(tempplt, histplt, size=(700, 300), margin=3UnitfulPlots.mm)
+savefig("posterior.png")

### 2022-03-17 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@64381af074f3e728fd9ea4ee40d6a3f206792be7 🚀

@@
 
+\begin{itemize}
+\tightlist
+\item
+  what are neutral landsacpes
+\end{itemize}
+
 Neutral landscapes are increasingly used in ecological and evolutionary
-studies to provide a null expectation spatial variation of a given
-measurement. Originally developed to simulate the spatially
-autocorrelated data (Gardner \emph{et al.} 1987; Milne 1992), the have
-seen use in a wide range of disciplines: from landscape genetics
-(Storfer \emph{et al.} 2007), to landscape and spatial ecology (Tinker
-\emph{et al.} 2004; Remmel \& Fortin 2013), and biogeography (Albert
-\emph{et al.} 2017).
+studies to provide a null expectation spatial variation of some
+measurement.
 
-We present \texttt{NeutralLandscapes.jl}, a package in \texttt{Julia}
-for neutral landscapes. The two primary packages used to simulate
-neutral landscapes are \texttt{NLMR} in (the \texttt{R} language)
-(Sciaini \emph{et al.} 2018) and \texttt{NLMpy} (in Python; Etherington
-\emph{et al.} 2015). Here we demonstrate that
-\texttt{NeutralLandscapes.jl}, depending on the method, is orders of
-magnitude faster than previous neutral landscape packages.
+Originally based around methods for simulating spatially autocorrelated
+data (Gardner \emph{et al.} 1987; Milne 1992).
+
+whawt is spaital autocorrelation
+
+they have seen use in a wide range of fields in ecology and evolution:
+from landscape genetics (Storfer \emph{et al.} 2007), to landscape and
+spatial ecology (Tinker \emph{et al.} 2004; Remmel \& Fortin 2013), and
+biogeography (Albert \emph{et al.} 2017).
+
+The two most popular libraries used to simulate neutral landscapes are
+\texttt{NLMR} in (the \texttt{R} language) (Sciaini \emph{et al.} 2018)
+and \texttt{NLMpy} (in Python; Etherington \emph{et al.} 2015). Here we
+present \texttt{NeutralLandscapes.jl}, a package for neutral landscape
+simulation in the \texttt{Julia} language. So, why another package? Here
+we demonstrate that \texttt{NeutralLandscapes.jl} is orders of magnitude
+faster than previous neutral landscape packages. In addition,
+\texttt{NeutralLandscapes.jl} implements several novel methods for
+simulating environmental change with temporal variation.
 
@@
 change and its consequences, its clear there is a gap in methodology in
-generating neutral landscapes that change over time. In addition we
-present a novel method for generating landscape change with prescribed
-levels of spatial and temporal autocorrelation, which is implemented in
-\texttt{NeutralLandscapes.jl}
+generating neutral landscapes that change over time. Our model allows
+users to simulate time-series of any \texttt{NeutralLandscape} layer,
+and which produce an arbitrary distribution of change across every
+spatial cell, with provided levels of spatial and temporal
+autocorrelation.
 
@@
 
+Further, \texttt{NL.jl} provides methods for interacting with other
+\texttt{julia} packages, and functions for rescaling
+
 \hypertarget{interoperability}{%
@@
 quebec = SimpleSDMPredictor(WorldClim, BioClim; left=-90., right=-50., top=75., bottom=40.)
-qcmask = fill(true, size(quebec))
-qcmask[findall(isnothing, quebec.grid)] .= false
+qcmask = fill(true, size(quebec))                   # ------ TODO
+qcmask[findall(isnothing, quebec.grid)] .= false    # should both of these lines be possible only using mask?
 
@@
 
+\hypertarget{rescaling-to-mimic-real-data}{%
+\subsection{Rescaling to mimic real
+data}\label{rescaling-to-mimic-real-data}}
+
+Figure: Real temp (left) / Rescaled NL (right) , same unit bar
+
+\hypertarget{generating-dynamic-neutral-landscapes}{%
+\subsection{Generating dynamic neutral
+landscapes}\label{generating-dynamic-neutral-landscapes}}
+
+We implement methods for generating change that are temporally
+autocorrelated, spatially-autocorrelated, or both.
+
+\(M_t = M_{t-1} + f(M(t-1))\)
+
+\hypertarget{models-of-change}{%
+\subsection{Models of change}\label{models-of-change}}
+
+Two types of temporal change: (1) null change, where the is random
+variation in each cell across time but the mean value across all cells
+stays constant (with some variation around this constant due to
+randomness in change generation)
+
+\hypertarget{null}{%
+\subsubsection{Null}\label{null}}
+
+Take an arbitrary distribution (from \texttt{Distributions.jl}) and set
+its mean value to 0, and apply draws from that distribution to each cell
+at each timestep.
+
+\hypertarget{directional}{%
+\subsubsection{Directional}\label{directional}}
+
+Can take an arbitrary distribution of values and set its expected-value
+to be the primary input into a change model---the mean amount of change
+at each timestep. This can also be parameterized to a be a variable list
+of mean change at each corresponding timestep.
+
+\hypertarget{temporally-autocorrelation}{%
+\paragraph{Temporally
+autocorrelation}\label{temporally-autocorrelation}}
+
+We generate temporally autocorrelated change using the method. We take
+an arbitrary distribution \(A\)
+
+\(r\): rate, \(v\): variability, \(U\) matrix of draws from standard
+\(\text{Normal}(0,1)\). Here \(v\) replects the amount of temporal
+autocorrelation.
+
+The value of a given cell \((i,j)\) with value \(M_{ij}\)
+\[M_{ij}(t+1) = f_{T}(M_{ij}(t)) = r + vA_{ij}\]
+
+Results in an expected value of change of \(r\) per timestep with
+variance \(v\).
+
+\hypertarget{spatial-autocorrelation}{%
+\paragraph{Spatial autocorrelation}\label{spatial-autocorrelation}}
+
+Generate a matrix \(\delta\) with a NL generator.
+
+\(r\): rate, \(v\): variability, \([Z(\delta)]_{ij}\): the \((i,j)\)
+entry of the z-score of the \(\delta\) matrix
+
+Z-score is arbitrary and can be replaced with any dist.
+
+\(f_{S}(M_{ij}) = r + v \cdot [Z(\delta)]_{ij}\)
+
+\hypertarget{spatiotemporal-autocorrelation}{%
+\paragraph{Spatiotemporal
+autocorrelation}\label{spatiotemporal-autocorrelation}}
+
+Finally, to implement change this is both spatially and temporally
+autocorrelated
+
+\(f_{ST}(M_{ij}) = r + v \cdot [Z(\delta)]_{ij}\)
+
+\begin{figure}
+\centering
+\includegraphics{./figures/temporal.png}
+\caption{todo}
+\end{figure}
+
 \hypertarget{benchmark-comparison-to-nlmpy-and-nlmr}{%
@@
 
-\hypertarget{generating-dynamic-neutral-landscapes}{%
-\section{Generating dynamic neutral
-landscapes}\label{generating-dynamic-neutral-landscapes}}
+How many lines of code, and what language is that code in for each pkg?
+\texttt{NLMR} contains 893 lines of R, and 376+51 lines of C++.
+\texttt{nlmpy} contains 386 lines of python. Julia contains 664 lines of
+(non-test) \texttt{julia}. Note these numbers refer only to lines of
+code and not comments.
 
-We implement methods for generating change that are temporally
-autocorrelated, spatially-autocorrelated, or both.
+\hypertarget{example-fitting-a-neutral-landscape-to-an-empirical-spatial-dataset}{%
+\section{Example: fitting a neutral landscape to an empirical spatial
+dataset}\label{example-fitting-a-neutral-landscape-to-an-empirical-spatial-dataset}}
 
-\(M_t = M_{t-1} + f(M(t-1))\)
+Here we use approximate bayesian computation to estimate the parameter
+of autocorrelation H for an empirical raster of temperature data.
 
-\hypertarget{models-of-change}{%
-\subsection{Models of change}\label{models-of-change}}
+Why? What if we are interested in differentiating the processes that
+occur in this \emph{real} landscape versus landscapes with \emph{similar
+statistical properties}.
 
-\hypertarget{directional}{%
-\subsubsection{Directional}\label{directional}}
+We take a raster of mean temp around the st lawrence lowlands in QC, and
+use ABC to estimate the value of H under the midpoint-displacement
+model.
 
-\hypertarget{temporally-autocorrelation}{%
-\subsubsection{Temporally
-autocorrelation}\label{temporally-autocorrelation}}
-
-\(r\): rate, \(v\): variability, \(U\) matrix of draws from standard
-\(\text{Normal}(0,1)\).
-
-Here \(v\) replects the amount of temporal autocorrelation.
-
-\(f_{T}(M_{ij}) = r + vU_{ij}\)
-
-Results in an expected value of change of \(r\) per timestep with
-variance \(v\).
-
-\hypertarget{spatial-autocorrelation}{%
-\subsubsection{Spatial autocorrelation}\label{spatial-autocorrelation}}
-
-Generate a matrix \(\delta\) with a NL generator.
-
-\(r\): rate, \(v\): variability, \([Z(\delta)]_{ij}\): the \((i,j)\)
-entry of the zscore of the \(\delta\) matrix
-
-\(f_{S}(M_{ij}) = r + v \cdot [Z(\delta)]_{ij}\)
-
-\hypertarget{spatiotemporal-autocorrelation}{%
-\subsubsection{Spatiotemporal
-autocorrelation}\label{spatiotemporal-autocorrelation}}
-
-\(f_{ST}(M_{ij}) = r + v \cdot [Z(\delta)]_{ij}\)
+We use the variogram as the loss function
 
 \begin{figure}
+\hypertarget{fig:post}{%
 \centering
-\includegraphics{./figures/temporal.png}
-\caption{todo}
+\includegraphics{./figures/posterior.png}
+\caption{todo}\label{fig:post}
+}
 \end{figure}
-
-\hypertarget{rescaling-to-mimic-real-data}{%
-\subsection{Rescaling to mimic real
-data}\label{rescaling-to-mimic-real-data}}
 
@@
 \section{Discussion}\label{discussion}}
+
+Why is it good that we've made this a faster thing to do? Why are models
+of temporal change necessary? What can simulation do for spatial ecology
+more generally?
+
+What are questions we can address with NL.jl that was not possible
+before?
 

### 2022-04-05 src/04_inference.jl
some figure updates

@@ -96,13 +96,13 @@ using Plots, CSV, DataFrames
 
 df = CSV.read("./src/posterior_H.csv", DataFrame)
 
-histplt =histogram(df.posterior_H, legend=:topleft, label="Posterior", bins=0:0.01:1, normalize=:probability, fc=:steelblue4, fa=0.5, frame=:box, size=(500,500), dpi=300, xlim=(0,1))
+histplt =histogram(df.posterior_H, lw=0.5, legend=:topleft, label="Posterior", bins=0:0.01:1, normalize=:probability, fc=:dodgerblue, fa=0.5, frame=:box, size=(500,500), dpi=300, xlim=(0,1))
 hline!([0.01], label="Prior", lw=2, c=:forestgreen)
 
 xlabel!("H")
 ylabel!("Probability")
 
 
-using UnitfulPlots
-plot(tempplt, histplt, size=(700, 300), margin=3UnitfulPlots.mm)
+using Plots.PlotMeasures: mm
+plot(tempplt, histplt, size=(750, 400), margin=3mm)
 savefig("posterior.png")

### 2022-04-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@95f860b21612964841ed3849c3f84a0c23d5992b 🚀

@@
 \item
-  what are neutral landsacpes
+  what are neutral landscapes
 \end{itemize}
@@
 
-Originally based around methods for simulating spatially autocorrelated
+Different properties of landscapes (elevation, land cover, temperature)
+vary across space in non-random ways. Tobler's law of geography:
+``everything is related to everything else, but near things are more
+related than distant things''
+
+Originally based around methods for simulating spatially auto-correlated
 data (Gardner \emph{et al.} 1987; Milne 1992).
 
-whawt is spaital autocorrelation
+they have seen use in a wide range of fields in ecology and evolution:
+from landscape genetics (Storfer \emph{et al.} 2007), to spatial ecology
+(Tinker \emph{et al.} 2004; Remmel \& Fortin 2013), and biogeography
+(Albert \emph{et al.} 2017).
 
-they have seen use in a wide range of fields in ecology and evolution:
-from landscape genetics (Storfer \emph{et al.} 2007), to landscape and
-spatial ecology (Tinker \emph{et al.} 2004; Remmel \& Fortin 2013), and
-biogeography (Albert \emph{et al.} 2017).
-
-The two most popular libraries used to simulate neutral landscapes are
+The two most popular libraries used to generate neutral landscapes are
 \texttt{NLMR} in (the \texttt{R} language) (Sciaini \emph{et al.} 2018)
 and \texttt{NLMpy} (in Python; Etherington \emph{et al.} 2015). Here we
-present \texttt{NeutralLandscapes.jl}, a package for neutral landscape
-simulation in the \texttt{Julia} language. So, why another package? Here
-we demonstrate that \texttt{NeutralLandscapes.jl} is orders of magnitude
-faster than previous neutral landscape packages. In addition,
-\texttt{NeutralLandscapes.jl} implements several novel methods for
-simulating environmental change with temporal variation.
+present \texttt{NeutralLandscapes.jl}, a new package for neutral
+landscape simulation in the \texttt{Julia} language. So, why create
+another package?
 
-As biodiversity science becomes increasingly concerned with temporal
-change and its consequences, its clear there is a gap in methodology in
+Here we demonstrate that \texttt{NeutralLandscapes.jl} is orders of
+magnitude faster than previous neutral landscape packages.
+
+In addition, \texttt{NeutralLandscapes.jl} implements several novel
+methods for simulating environmental change with temporal variation. As
+biodiversity science becomes increasingly concerned with temporal change
+and its consequences, its clear there is a gap in methodology in
 generating neutral landscapes that change over time. Our model allows
 users to simulate time-series of any \texttt{NeutralLandscape} layer,
-and which produce an arbitrary distribution of change across every
+and which can produce an arbitrary distribution of change across every
 spatial cell, with provided levels of spatial and temporal

### 2022-08-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@d123368947355692a8697d9cdbd3a458554ee464 🚀

@@
 
-\hypertarget{example-fitting-a-neutral-landscape-to-an-empirical-spatial-dataset}{%
+\hypertarget{example-fitting-a-neutral-landscape-to-an-empirical-spatial-dataset-using-generative-modeling}{%
 \section{Example: fitting a neutral landscape to an empirical spatial
-dataset}\label{example-fitting-a-neutral-landscape-to-an-empirical-spatial-dataset}}
+dataset using generative
+modeling}\label{example-fitting-a-neutral-landscape-to-an-empirical-spatial-dataset-using-generative-modeling}}
 
